\chapter*{Glossary}
\phantomsection
\addcontentsline{toc}{chapter}{Glossary}



\subsubsection*{Abandon}
\addcontentsline{toc}{subsubsection}{Abandon}

To turn a face-up ongoing scheme card face down and put it on the bottom of its owner’s scheme deck. See rule 701.33, “Abandon.”

\subsubsection*{Ability}
\addcontentsline{toc}{subsubsection}{Ability}

Text on an object that explains what that object does or can do.
An activated or triggered ability on the stack. This kind of ability is an object.
See rule 113, “Abilities,” and section 6, “Spells, Abilities, and Effects.”

\subsubsection*{Ability Word}
\addcontentsline{toc}{subsubsection}{Ability Word}

An italicized word with no rules meaning that ties together abilities on different cards that have similar functionality. See rule 207.2c.

\subsubsection*{Absorb}
\addcontentsline{toc}{subsubsection}{Absorb}

A keyword ability that prevents damage. See rule 702.64, “Absorb.”

\subsubsection*{Activate}
\addcontentsline{toc}{subsubsection}{Activate}

To put an activated ability onto the stack and pay its costs, so that it will eventually resolve and have its effect. See rule 602, “Activating Activated Abilities.”

\subsubsection*{Activated Ability}
\addcontentsline{toc}{subsubsection}{Activated Ability}

A kind of ability. Activated abilities are written as “[Cost]: [Effect.] [Activation instructions (if any).]” See rule 113, “Abilities,” and rule 602, “Activating Activated Abilities.”

\subsubsection*{Activation Cost}
\addcontentsline{toc}{subsubsection}{Activation Cost}

Everything that appears before the colon in an activated ability’s text. It must be paid to activate the ability. See rule 118, “Costs,” and rule 602, “Activating Activated Abilities.”

\subsubsection*{Active Player}
\addcontentsline{toc}{subsubsection}{Active Player}

The player whose turn it is. See rule 102.1.

\subsubsection*{Active Player, Nonactive Player Order}
\addcontentsline{toc}{subsubsection}{Active Player, Nonactive Player Order}

A system that determines the order by which players make choices if multiple players are instructed to make choices at the same time. See rule 101.4. This rule is modified for games using the shared team turns option; see rule 805.6.

\subsubsection*{Active Team}
\addcontentsline{toc}{subsubsection}{Active Team}

The team whose turn it is in a game using the shared team turns option. See rule 805.4a.

\subsubsection*{Adapt}
\addcontentsline{toc}{subsubsection}{Adapt}

A keyword action that puts +1/+1 counters on a creature that doesn’t have any yet. See rule 701.46, “Adapt.”

\subsubsection*{Additional Cost}
\addcontentsline{toc}{subsubsection}{Additional Cost}

A cost a spell may have that its controller may pay (or, in some cases, must pay) in addition to its mana cost to cast that spell. See rule 118, “Costs,” and rule 601, “Casting Spells.”

\subsubsection*{Adventurer Card}
\addcontentsline{toc}{subsubsection}{Adventurer Card}

Cards with a two-part card frame (one part of which is inset on the left) on a single card where the alternative characteristics include the Adventure spell type. See rule 715, “Adventurer Cards.”

\subsubsection*{Affinity}
\addcontentsline{toc}{subsubsection}{Affinity}

A keyword ability that reduces how much mana you need to spend to cast a spell. See rule 702.41, “Affinity.”

\subsubsection*{Afflict}
\addcontentsline{toc}{subsubsection}{Afflict}

A keyword ability that makes the defending player lose life for blocking. See rule 702.130, “Afflict.”

\subsubsection*{Afterlife}
\addcontentsline{toc}{subsubsection}{Afterlife}

A keyword ability that leaves behind Spirit creature tokens when certain creatures die. See rule 702.135, “Afterlife.”

\subsubsection*{Aftermath}
\addcontentsline{toc}{subsubsection}{Aftermath}

A keyword ability that lets a player cast one half of a split card only from their graveyard. See rule 702.127, “Aftermath.”

\subsubsection*{Airbend}
\addcontentsline{toc}{subsubsection}{Airbend}

A keyword action that exiles one or more permanents and/or spells. The owner of each card exiled with airbend may cast it from exile by paying {2 rather than paying its mana cost. See rule 701.65, “Airbend.”

\subsubsection*{Alternating Teams Variant}
\addcontentsline{toc}{subsubsection}{Alternating Teams Variant}

A multiplayer variant played among two or more teams of equal size. See rule 811, “Alternating Teams Variant.”

\subsubsection*{Alternative Cost}
\addcontentsline{toc}{subsubsection}{Alternative Cost}

A cost a spell may have that its controller can pay rather than paying its mana cost. See rule 118, “Costs,” and rule 601, “Casting Spells.”

\subsubsection*{Alternate Name}
\addcontentsline{toc}{subsubsection}{Alternate Name}

A different name used on promotional or alternate-art versions of some cards. This name has no rules meaning. See rule 201.6.

\subsubsection*{Amass}
\addcontentsline{toc}{subsubsection}{Amass}

A keyword action that gives you a Zombie Army creature token or grows an Army you already have. See rule 701.47, “Amass.”

\subsubsection*{Amplify}
\addcontentsline{toc}{subsubsection}{Amplify}

A keyword ability than can have a creature enter the battlefield with +1/+1 counters on it. See rule 702.38, “Amplify.”

\subsubsection*{Anchor Word}
\addcontentsline{toc}{subsubsection}{Anchor Word}

A word that precedes one of two abilities a permanent may enter the battlefield with. See rule 614.12b.

\subsubsection*{Annihilator}
\addcontentsline{toc}{subsubsection}{Annihilator}

A keyword ability that can make a creature particularly brutal when it attacks. See rule 702.86, “Annihilator.”

\subsubsection*{Ante}
\addcontentsline{toc}{subsubsection}{Ante}

A zone used only when playing “for keeps.”
To put a card into the ante zone.
See rule 407, “Ante.”

\subsubsection*{Any Target}
\addcontentsline{toc}{subsubsection}{Any Target}

A spell or ability may require “any target.” “Any target” is the same as “target creature, player, or planeswalker.” See rule 115.4.

\subsubsection*{APNAP Order}
\addcontentsline{toc}{subsubsection}{APNAP Order}

See Active Player, Nonactive Player Order.

\subsubsection*{Archenemy}
\addcontentsline{toc}{subsubsection}{Archenemy}

A casual variant in which a team of players faces off against a single opponent strengthened with powerful scheme cards. See rule 904, “Archenemy.”
A player in an Archenemy game who is playing with a scheme deck.

\subsubsection*{Archenemy Commander}
\addcontentsline{toc}{subsubsection}{Archenemy Commander}

A Commander game that follows a modified version of the Archenemy rules. See rule 903, “Commander,” and rule 904, “Archenemy.”

\subsubsection*{Artifact}
\addcontentsline{toc}{subsubsection}{Artifact}

A card type. An artifact is a permanent. See rule 301, “Artifacts.”

\subsubsection*{Artifact Creature}
\addcontentsline{toc}{subsubsection}{Artifact Creature}

A combination of artifact and creature that’s subject to the rules for both. See rule 301, “Artifacts,” and rule 302, “Creatures.”

\subsubsection*{Artifact Land}
\addcontentsline{toc}{subsubsection}{Artifact Land}

A combination of artifact and land that’s subject to the rules for both. Artifact lands can only be played as lands, not cast as spells. See rule 301, “Artifacts,” and rule 305, “Lands.”

\subsubsection*{Artifact Type}
\addcontentsline{toc}{subsubsection}{Artifact Type}

A subtype that’s correlated to the artifact card type. See rule 301, “Artifacts.” See rule 205.3g for the list of artifact types.

\subsubsection*{As Though}
\addcontentsline{toc}{subsubsection}{As Though}

Text used to indicate that the game, for some specific purpose, treats a condition as true even though it’s not. See rule 609.4.

\subsubsection*{Ascend}
\addcontentsline{toc}{subsubsection}{Ascend}

A keyword causing a player to get the designation of the city’s blessing once they control ten permanents. See rule 702.131, “Ascend.”

\subsubsection*{Assemble}
\addcontentsline{toc}{subsubsection}{Assemble}

Assemble is a keyword action in the Unstable set that puts Contraptions onto the battlefield. Cards and mechanics from the Unstable set aren’t included in these rules.

\subsubsection*{Assign Combat Damage}
\addcontentsline{toc}{subsubsection}{Assign Combat Damage}

To determine how an attacking or blocking creature will deal its combat damage. See rule 510, “Combat Damage Step.”

\subsubsection*{Assist}
\addcontentsline{toc}{subsubsection}{Assist}

A keyword ability that lets another player help you pay for a spell. See rule 702.132, “Assist.”

At End of Turn (Obsolete)

A trigger condition printed on abilities that triggered at the beginning of the end step (which is not the last thing to happen in the turn). Cards that were printed with that text have received errata in the Oracle card reference to say “at the beginning of the end step” or “at the beginning of the next end step.” See rule 513, “End Step.”

\subsubsection*{Attach}
\addcontentsline{toc}{subsubsection}{Attach}

To take an Aura, Equipment, or Fortification from where it currently is and put it onto a specified object or player. See rule 701.3, “Attach.”

\subsubsection*{Attack}
\addcontentsline{toc}{subsubsection}{Attack}

To send a creature into combat offensively. A creature can attack a player or a planeswalker. See rule 508, “Declare Attackers Step.”

\subsubsection*{Attack Alone}
\addcontentsline{toc}{subsubsection}{Attack Alone}

A creature “attacks alone” if it’s the only creature declared as an attacker during the declare attackers step. A creature “is attacking alone” if it’s attacking but no other creatures are. See rule 506.5.

\subsubsection*{Attack Left Option}
\addcontentsline{toc}{subsubsection}{Attack Left Option}

An option that may be used in certain multiplayer variants. See rule 803, “Attack Left and Attack Right Options.”

\subsubsection*{Attack Multiple Players Option}
\addcontentsline{toc}{subsubsection}{Attack Multiple Players Option}

An option that may be used in certain multiplayer variants. See rule 802, “Attack Multiple Players Option.”

\subsubsection*{Attack Right Option}
\addcontentsline{toc}{subsubsection}{Attack Right Option}

An option that may be used in certain multiplayer variants. See rule 803, “Attack Left and Attack Right Options.”

\subsubsection*{Attacking Creature}
\addcontentsline{toc}{subsubsection}{Attacking Creature}

A creature that has either been declared as part of a legal attack during the combat phase (once all costs to attack, if any, have been paid), or a creature that has been put onto the battlefield attacking. It remains an attacking creature until it’s removed from combat or the combat phase ends, whichever comes first. See rule 508, “Declare Attackers Step.”

\subsubsection*{Attacking Team}
\addcontentsline{toc}{subsubsection}{Attacking Team}

The team who can attack during the combat phase of a multiplayer game using the shared team turns option. See rule 805, “Shared Team Turns Option.”

\subsubsection*{Attacks and Isn’t Blocked}
\addcontentsline{toc}{subsubsection}{Attacks and Isn’t Blocked}

An ability that triggers when a creature “attacks and isn’t blocked” triggers when the creature becomes an unblocked attacking creature. See rule 509.1h.

\subsubsection*{Attraction}
\addcontentsline{toc}{subsubsection}{Attraction}

An artifact type seen only on nontraditional Magic cards in the Unfinity expansion. See rule 717, “Attraction Cards,” rule 701.51, “Open an Attraction,” and rule 701.52, “Roll to Visit Your Attractions.”

\subsubsection*{Attraction Deck}
\addcontentsline{toc}{subsubsection}{Attraction Deck}

An optional deck of at least three (in limited play) or ten (in constructed play) Attraction cards that can be used to support play with some cards from the Unfinity expansion. See rule 717.2.

\subsubsection*{Aura}
\addcontentsline{toc}{subsubsection}{Aura}

An enchantment subtype. Aura spells target objects or players, and Aura permanents are attached to objects or players. See rule 303, “Enchantments,” and rule 702.5, “Enchant.”

\subsubsection*{Aura Swap}
\addcontentsline{toc}{subsubsection}{Aura Swap}

A keyword ability that lets you exchange an Aura on the battlefield with one in your hand. See rule 702.65, “Aura Swap.”

\subsubsection*{Awaken}
\addcontentsline{toc}{subsubsection}{Awaken}

A keyword ability that lets you turn a land you control into a creature. See rule 702.113, “Awaken.”

\subsubsection*{Background}
\addcontentsline{toc}{subsubsection}{Background}

An enchantment type that, in combination with the “choose a Background” ability, may allow a legendary enchantment card to be your commander. See rule 702.124, “Partner,” and rule 903, “Commander.”

\subsubsection*{Backup}
\addcontentsline{toc}{subsubsection}{Backup}

A keyword ability that lets a creature give +1/+1 counters to itself or another when it enters the battlefield. If a different creature is chosen, that creature also temporarily gains one or more abilities. See rule 702.165, “Backup.”

\subsubsection*{Banding, “Bands with Other”}
\addcontentsline{toc}{subsubsection}{Banding, “Bands with Other”}

Banding is a keyword ability that modifies the rules for declaring attackers and assigning combat damage. “Bands with other” is a specialized version of the ability. See rule 702.22, “Banding.”

\subsubsection*{Bargain}
\addcontentsline{toc}{subsubsection}{Bargain}

Bargain is a keyword ability that represents an optional additional cost of sacrificing an artifact, enchantment, or token. A spell has been bargained if its controller declared the intention to pay that cost. See rule 702.166, “Bargain.”

\subsubsection*{Base Power, Base Toughness}
\addcontentsline{toc}{subsubsection}{Base Power, Base Toughness}

Effects that change the base power and/or base toughness of a creature set one or both of those values to a specific number. See rule 613, “Interaction of Continuous Effects.”

\subsubsection*{Basic}
\addcontentsline{toc}{subsubsection}{Basic}

A supertype that’s normally relevant on lands. Any land with this supertype is a basic land. See rule 205.4, “Supertypes.”

\subsubsection*{Basic Landcycling}
\addcontentsline{toc}{subsubsection}{Basic Landcycling}

See Typecycling.

\subsubsection*{Basic Land Type}
\addcontentsline{toc}{subsubsection}{Basic Land Type}

There are five “basic land types”: Plains, Island, Swamp, Mountain, and Forest. Each one has a mana ability associated with it. See rule 305, “Lands.”

\subsubsection*{Battle}
\addcontentsline{toc}{subsubsection}{Battle}

A card type. A battle is a permanent. See rule 310, “Battles.”

\subsubsection*{Battle Cry}
\addcontentsline{toc}{subsubsection}{Battle Cry}

A keyword ability that makes other attacking creatures better in combat. See rule 702.91, “Battle Cry.”

\subsubsection*{Battlefield}
\addcontentsline{toc}{subsubsection}{Battlefield}

A zone. The battlefield is the zone in which permanents exist. It used to be known as the “in-play” zone. See rule 403, “Battlefield.”

\subsubsection*{Becomes}
\addcontentsline{toc}{subsubsection}{Becomes}

A word used in some trigger events to indicate a change in status or characteristics. See rule 603.2e.

\subsubsection*{Beginning of Combat Step}
\addcontentsline{toc}{subsubsection}{Beginning of Combat Step}

Part of the turn. This step is the first step of the combat phase. See rule 507, “Beginning of Combat Step.”

\subsubsection*{Beginning Phase}
\addcontentsline{toc}{subsubsection}{Beginning Phase}

Part of the turn. This phase is the first phase of the turn. See rule 501, “Beginning Phase.”

\subsubsection*{Behold}
\addcontentsline{toc}{subsubsection}{Behold}

A keyword action that allows a player to choose a permanent they control of a particular quality or reveal a card of that quality from their hand, usually to pay a cost or get an additional effect. See rule 701.4, “Behold.”

\subsubsection*{Bestow}
\addcontentsline{toc}{subsubsection}{Bestow}

A keyword ability that lets a creature card be cast as an Aura. See rule 702.103, “Bestow.”

\subsubsection*{Blight}
\addcontentsline{toc}{subsubsection}{Blight}

A keyword action. To blight N means to put N -1/-1 counters on a creature you control. See rule 701.68, “Blight.”

\subsubsection*{Blitz}
\addcontentsline{toc}{subsubsection}{Blitz}

A keyword ability found on creature cards that allows them to be cast for an alternative cost. See rule 702.152, “Blitz.”

\subsubsection*{Block}
\addcontentsline{toc}{subsubsection}{Block}

To send a creature into combat defensively. A creature can block an attacking creature. See rule 509, “Declare Blockers Step.”

\subsubsection*{Block Alone}
\addcontentsline{toc}{subsubsection}{Block Alone}

A creature “blocks alone” if it’s the only creature declared as a blocker during the declare blockers step. A creature “is blocking alone” if it’s blocking but no other creatures are. See rule 506.5.

\subsubsection*{Blocked Creature}
\addcontentsline{toc}{subsubsection}{Blocked Creature}

An attacking creature that another creature blocks or that an effect causes to become blocked. It remains a blocked creature until it’s removed from combat, an effect says that it becomes unblocked, or the combat phase ends, whichever comes first. See rule 509, “Declare Blockers Step.”

\subsubsection*{Blocking Creature}
\addcontentsline{toc}{subsubsection}{Blocking Creature}

A creature that has either been declared as part of a legal block during the combat phase (once all costs to block, if any, have been paid), or a creature that has been put onto the battlefield blocking. It remains a blocking creature until it’s removed from combat or the combat phase ends, whichever comes first. See rule 509, “Declare Blockers Step.”

\subsubsection*{Blood Token}
\addcontentsline{toc}{subsubsection}{Blood Token}

A Blood token is a colorless artifact token with “{1, {T, Discard a card, Sacrifice this token: Draw a card.” For more information about predefined tokens, see rule 111.10.

\subsubsection*{Bloodthirst}
\addcontentsline{toc}{subsubsection}{Bloodthirst}

A keyword ability that can have a creature enter the battlefield with +1/+1 counters on it. See rule 702.54, “Bloodthirst.”

\subsubsection*{Boast}
\addcontentsline{toc}{subsubsection}{Boast}

A special kind of activated ability that can be activated only once each turn if the creature with the boast ability attacked that turn. See rule 702.142, “Boast.”

\subsubsection*{Bolster}
\addcontentsline{toc}{subsubsection}{Bolster}

A keyword action that puts +1/+1 counters on the weakest creature a player controls. See rule 701.39, “Bolster.”

\subsubsection*{Booster Pack}
\addcontentsline{toc}{subsubsection}{Booster Pack}

A group of unopened Magic cards from a particular expansion. Booster packs are used in Limited formats. See rule 100.2b.

\subsubsection*{Brawl}
\addcontentsline{toc}{subsubsection}{Brawl}

An option for the Commander casual variant. See rule 903.12, “Brawl Option.”

\subsubsection*{Bury (Obsolete)}
\addcontentsline{toc}{subsubsection}{Bury (Obsolete)}

A term that meant “put [a permanent] into its owner’s graveyard.” In general, cards that were printed with the term “bury” have received errata in the Oracle card reference to read, “Destroy [a permanent]. It can’t be regenerated,” or “Sacrifice [a permanent].”

\subsubsection*{Bushido}
\addcontentsline{toc}{subsubsection}{Bushido}

A keyword ability that can make a creature better in combat. See rule 702.45, “Bushido.”

\subsubsection*{Buyback}
\addcontentsline{toc}{subsubsection}{Buyback}

A keyword ability of instants and sorceries that can let the spell return to its owner’s hand as it resolves. See rule 702.27, “Buyback.”

\subsubsection*{Card}
\addcontentsline{toc}{subsubsection}{Card}

The standard component of the game. Magic cards may be traditional or nontraditional. Tokens aren’t considered cards. In the text of spells or abilities, the term “card” is used only to refer to a card that’s not on the battlefield or on the stack, such as a creature card in a player’s hand. See rule 108, “Cards.”

\subsubsection*{Card Pool}
\addcontentsline{toc}{subsubsection}{Card Pool}

In a Limited format, the cards a player may use, in addition to basic land cards, to build their deck.

\subsubsection*{Card Type}
\addcontentsline{toc}{subsubsection}{Card Type}

A characteristic. Except for abilities on the stack, each object has a card type, even if that object isn’t a card. Each card type has its own rules. See rule 205, “Type Line,” and section 3, “Card Types.”

\subsubsection*{Cascade}
\addcontentsline{toc}{subsubsection}{Cascade}

A keyword ability that may let a player cast a random extra spell for no cost. See rule 702.85, “Cascade.”

\subsubsection*{Case}
\addcontentsline{toc}{subsubsection}{Case}

An enchantment subtype. Cases have a “to solve” ability that set a condition its controller must meet in order for the “solved” ability to take effect. See rule 719, “Case Cards.”

\subsubsection*{Cast}
\addcontentsline{toc}{subsubsection}{Cast}

To take a card from where it is (usually the hand), put it on the stack, and pay its costs, so that it will eventually resolve and have its effect. See rule 601, “Casting Spells.”

\subsubsection*{Caster (Obsolete)}
\addcontentsline{toc}{subsubsection}{Caster (Obsolete)}

An obsolete term that referred to the player who cast a spell. In general, cards that were printed with the term “caster” have received errata in the Oracle card reference to say “controller.”

\subsubsection*{Casting Cost (Obsolete)}
\addcontentsline{toc}{subsubsection}{Casting Cost (Obsolete)}

An obsolete term for mana cost. Cards printed with this text have received errata in the Oracle card reference.

\subsubsection*{Casualty}
\addcontentsline{toc}{subsubsection}{Casualty}

A keyword ability that allows you to sacrifice a creature to create a copy of a spell. See 702.153, “Casualty.”

\subsubsection*{Champion, Championed}
\addcontentsline{toc}{subsubsection}{Champion, Championed}

“Champion” is a keyword ability that lets one creature temporarily replace another. A permanent is “championed” by another permanent if the latter exiles the former as the direct result of a champion ability. See rule 702.72, “Champion.”

\subsubsection*{Change a Target}
\addcontentsline{toc}{subsubsection}{Change a Target}

To choose a new, legal target for a spell or ability. See rule 115.7.

\subsubsection*{Changeling}
\addcontentsline{toc}{subsubsection}{Changeling}

A characteristic-defining ability that grants the object it’s on every creature type. See rule 702.73, “Changeling.”

\subsubsection*{Chaos Ability}
\addcontentsline{toc}{subsubsection}{Chaos Ability}

An ability of a plane card that triggers “Whenever chaos ensues” in the Planechase casual variant. See rule 311.7.

\subsubsection*{Chaos Symbol}
\addcontentsline{toc}{subsubsection}{Chaos Symbol}

The chaos symbol appears on the planar die and near some triggered abilities of plane cards in the Planechase casual variant. See rule 107.12.

\subsubsection*{Characteristics}
\addcontentsline{toc}{subsubsection}{Characteristics}

Information that defines an object. See rule 109.3.

\subsubsection*{Characteristic-Defining Ability}
\addcontentsline{toc}{subsubsection}{Characteristic-Defining Ability}

A kind of static ability that conveys information about an object’s characteristics that would normally be found elsewhere on that object (such as in its mana cost, type line, or power/toughness box). See rule 604.3.

\subsubsection*{Choose a Background}
\addcontentsline{toc}{subsubsection}{Choose a Background}

A variant of the partner ability that lets two legendary permanent cards be your commander in the Commander variant rather than one if one of them has the “choose a Background” ability and the other is a Background enchantment card. See rule 702.124, “Partner,” and rule 903, “Commander.”

\subsubsection*{Cipher}
\addcontentsline{toc}{subsubsection}{Cipher}

A keyword ability that allows you to encode a card on a creature and cast that card whenever that creature deals combat damage to a player. See rule 702.99, “Cipher.”

\subsubsection*{City’s Blessing}
\addcontentsline{toc}{subsubsection}{City’s Blessing}

A designation a player can have. The ascend keyword causes a player to get this designation once they control ten permanents. See rule 702.131, “Ascend.”

\subsubsection*{Clash}
\addcontentsline{toc}{subsubsection}{Clash}

To have a mini-contest involving the top cards of players’ libraries. See rule 701.30, “Clash.”

\subsubsection*{Class}
\addcontentsline{toc}{subsubsection}{Class}

An enchantment subtype. Classes have a number of class level abilities that increase their level and grant them new abilities. See rule 716, “Class Cards.”

\subsubsection*{Cleanup Step}
\addcontentsline{toc}{subsubsection}{Cleanup Step}

Part of the turn. This step is the second and final step of the ending phase. See rule 514, “Cleanup Step.”

\subsubsection*{Cleave}
\addcontentsline{toc}{subsubsection}{Cleave}

A keyword ability that allows you to pay an alternative cost to remove some of a spell’s text. See rule 702.148, “Cleave.”

\subsubsection*{Cloak}
\addcontentsline{toc}{subsubsection}{Cloak}

A keyword action that puts a card onto the battlefield face down as a 2/2 creature with ward {2. See rule 701.58, “Cloak,” and rule 708, “Face-Down Spells and Permanents.”

\subsubsection*{Clue Token}
\addcontentsline{toc}{subsubsection}{Clue Token}

A Clue token is a colorless artifact token with “{2, Sacrifice this token: Draw a card.” For more information about predefined tokens, see rule 111.10.

\subsubsection*{Collect Evidence}
\addcontentsline{toc}{subsubsection}{Collect Evidence}

A keyword action. To “collect evidence N” means to exile any number of cards from your graveyard with total mana value N or greater. See rule 701.59, “Collect Evidence.”

\subsubsection*{Collector Number}
\addcontentsline{toc}{subsubsection}{Collector Number}

A number printed on most cards that has no effect on game play. See rule 213, “Information Below the Text Box.”

\subsubsection*{Color}
\addcontentsline{toc}{subsubsection}{Color}

A characteristic of an object. See rule 105, “Colors,” and rule 202, “Mana Cost and Color.”
An attribute mana may have. See rule 106, “Mana.”

\subsubsection*{Colorless}
\addcontentsline{toc}{subsubsection}{Colorless}

An object with no color is colorless. Colorless is not a color. See rule 105, “Colors,” and rule 202, “Mana Cost and Color.”
A type of mana. See rule 106, “Mana,” and rule 107.4c.

\subsubsection*{Color Identity}
\addcontentsline{toc}{subsubsection}{Color Identity}

A set of colors that determines what cards may be included in a deck for the Commander casual variant. See rule 903.4.

\subsubsection*{Color Indicator}
\addcontentsline{toc}{subsubsection}{Color Indicator}

A characteristic of an object. See rule 105, “Colors,” and rule 204, “Color Indicator.”

\subsubsection*{Combat Damage}
\addcontentsline{toc}{subsubsection}{Combat Damage}

Damage dealt during the combat damage step by attacking creatures and blocking creatures as a consequence of combat. See rule 510, “Combat Damage Step.”

\subsubsection*{Combat Damage Step}
\addcontentsline{toc}{subsubsection}{Combat Damage Step}

Part of the turn. This step is the fourth step of the combat phase. See rule 510, “Combat Damage Step.”

\subsubsection*{Combat Phase}
\addcontentsline{toc}{subsubsection}{Combat Phase}

Part of the turn. This phase is the third phase of the turn. See rule 506, “Combat Phase.”

\subsubsection*{Command}
\addcontentsline{toc}{subsubsection}{Command}

A zone for certain specialized objects that have an overarching effect on the game, yet are not permanents and cannot be destroyed. See rule 408, “Command.”

\subsubsection*{Commander}
\addcontentsline{toc}{subsubsection}{Commander}

A casual variant in which each deck is led by a legendary card (usually a creature). See rule 903, “Commander.”
A designation given to one legendary card in each player’s deck in the Commander casual variant.

\subsubsection*{Commander Draft}
\addcontentsline{toc}{subsubsection}{Commander Draft}

A casual variant in which players participate in a booster draft and then play multiplayer games. See rule 903.13, “Commander Draft.”

\subsubsection*{Commander Ninjutsu}
\addcontentsline{toc}{subsubsection}{Commander Ninjutsu}

A variant of the ninjutsu ability. See rule 702.49, “Ninjutsu.”

\subsubsection*{Commander Tax}
\addcontentsline{toc}{subsubsection}{Commander Tax}

Informal term for the additional cost to cast a commander based on the number of times a player has cast it previously this game. See rule 903.8.

\subsubsection*{Companion}
\addcontentsline{toc}{subsubsection}{Companion}

A keyword ability that allows a player to choose one creature card from outside the game as a companion if the restriction of that card’s companion ability is met. Once a player has chosen a companion, that player may pay {3 to put it into their hand once during the game. See rule 702.139, “Companion.”

\subsubsection*{Compleated}
\addcontentsline{toc}{subsubsection}{Compleated}

A keyword ability that causes a planeswalker to enter the battlefield with fewer loyalty counters if a player chose to pay life for Phyrexian mana symbols in its cost. See rule 702.150, “Compleated.”

\subsubsection*{Complete a Dungeon}
\addcontentsline{toc}{subsubsection}{Complete a Dungeon}

To remove a dungeon card from the game after reaching that dungeon card’s bottommost room. See rule 309, “Dungeons.”

\subsubsection*{Concede}
\addcontentsline{toc}{subsubsection}{Concede}

To quit the game. Conceding a game immediately causes that player to leave that game and lose that game. See rule 104, “Ending the Game.”

\subsubsection*{Connive}
\addcontentsline{toc}{subsubsection}{Connive}

A keyword action that causes a player to draw a card, discard a card, and then to put a +1/+1 counter on a creature if a nonland card was discarded this way. See rule 701.50, “Connive.”

\subsubsection*{Conspiracy}
\addcontentsline{toc}{subsubsection}{Conspiracy}

A card type used in Limited formats such as Conspiracy Draft. A conspiracy card is not a permanent. See rule 315, “Conspiracies.”

\subsubsection*{Conspiracy Draft}
\addcontentsline{toc}{subsubsection}{Conspiracy Draft}

A casual variant in which players participate in a booster draft and then play multiplayer games. See rule 905, “Conspiracy Draft.”

\subsubsection*{Conspire}
\addcontentsline{toc}{subsubsection}{Conspire}

A keyword ability that creates a copy of a spell. See rule 702.78, “Conspire.”

\subsubsection*{Constructed}
\addcontentsline{toc}{subsubsection}{Constructed}

A way of playing in which each player creates their own deck ahead of time. See rule 100.2a.

\subsubsection*{Continuous Effect}
\addcontentsline{toc}{subsubsection}{Continuous Effect}

An effect that modifies characteristics of objects, modifies control of objects, or affects players or the rules of the game, for a fixed or indefinite period. See rule 611, “Continuous Effects.”

\subsubsection*{Continuous Artifact (Obsolete)}
\addcontentsline{toc}{subsubsection}{Continuous Artifact (Obsolete)}

An obsolete term that appeared on the type line of artifacts without activated abilities. Cards printed with this text have received errata in the Oracle card reference to simply say “Artifact.”

\subsubsection*{Control, Controller}
\addcontentsline{toc}{subsubsection}{Control, Controller}

“Control” is the system that determines who gets to use an object in the game. An object’s “controller” is the player who currently controls it. See rule 108.4.

\subsubsection*{Control Another Player}
\addcontentsline{toc}{subsubsection}{Control Another Player}

To make all choices and decisions that player is allowed to make, or is told to make, by rules or by any objects. See rule 722, “Controlling Another Player.”

\subsubsection*{Convert}
\addcontentsline{toc}{subsubsection}{Convert}

To turn a double-faced card so its other face is up. See rule 701.28, “Convert.”

\subsubsection*{Converted Mana Cost (Obsolete)}
\addcontentsline{toc}{subsubsection}{Converted Mana Cost (Obsolete)}

An obsolete term for mana value. Cards printed with this term have received errata in the Oracle card reference.

\subsubsection*{Convoke}
\addcontentsline{toc}{subsubsection}{Convoke}

A keyword ability that lets you tap creatures rather than pay mana to cast a spell. See rule 702.51, “Convoke.”

\subsubsection*{Copiable Values}
\addcontentsline{toc}{subsubsection}{Copiable Values}

Values of an object’s characteristics that are checked by copy effects. See rules 613.2, 707.2, and 707.3.

\subsubsection*{Copy}
\addcontentsline{toc}{subsubsection}{Copy}

To create a new object whose copiable values have been set to those of another object.
An object whose copiable values have been set to those of another object.
See rule 707, “Copying Objects.”

\subsubsection*{Cost}
\addcontentsline{toc}{subsubsection}{Cost}

An action or payment necessary to take another action or to stop another action from taking place. See rule 118, “Costs.”

\subsubsection*{Counter}
\addcontentsline{toc}{subsubsection}{Counter}

To cancel a spell or ability so it doesn’t resolve and none of its effects occur. See rule 701.6, “Counter.”
A marker placed on an object or player that modifies its characteristics or interacts with a rule or ability. See rule 122, “Counters.”
Counts As (Obsolete)

Some older cards were printed with text stating that the card “counts as” something. Cards printed with this text have received errata in the Oracle card reference to state that the card actually is that thing.

\subsubsection*{Craft}
\addcontentsline{toc}{subsubsection}{Craft}

Craft is an activated ability that allows a player to exile cards from their graveyard and/or permanents they control to exile the permanent with the craft ability and return it onto the battlefield transformed. See rule 702.167, “Craft.”

\subsubsection*{Create}
\addcontentsline{toc}{subsubsection}{Create}

To create a token is to put a token onto the battlefield. See rule 701.7, “Create.”

\subsubsection*{Creature}
\addcontentsline{toc}{subsubsection}{Creature}

A card type. A creature is a permanent. See rule 302, “Creatures.”

\subsubsection*{Creature Type}
\addcontentsline{toc}{subsubsection}{Creature Type}

A subtype that’s correlated to the creature card type and the kindred card type. See rule 302, “Creatures,” and rule 308, “Kindreds.” See rule 205.3m for the list of creature types.

\subsubsection*{Crew}
\addcontentsline{toc}{subsubsection}{Crew}

A keyword ability that lets you tap creatures to turn a Vehicle into an artifact creature. See rule 301, “Artifacts,” and rule 702.122, “Crew.”

\subsubsection*{Crime}
\addcontentsline{toc}{subsubsection}{Crime}

Targeting an opponent, anything that opponent controls, and/or any cards in an opponent’s graveyard is a crime. See rule 700.13.

\subsubsection*{Cumulative Upkeep}
\addcontentsline{toc}{subsubsection}{Cumulative Upkeep}

A keyword ability that imposes an increasing cost to keep a permanent on the battlefield. See rule 702.24, “Cumulative Upkeep.”

\subsubsection*{Cycling}
\addcontentsline{toc}{subsubsection}{Cycling}

A keyword ability that lets a card be discarded and replaced with a new card. See rule 702.29, “Cycling.”

\subsubsection*{Damage}
\addcontentsline{toc}{subsubsection}{Damage}

Objects can deal “damage” to creatures, planeswalkers, and players. This is generally detrimental to the object or player that receives that damage. See rule 120, “Damage.”

\subsubsection*{Damage Assignment Order (Obsolete)}
\addcontentsline{toc}{subsubsection}{Damage Assignment Order (Obsolete)}

Previously, if a creature blocks or becomes blocked by multiple creatures, the creature’s controller would be required to choose an order in which it would assign combat damage to the creatures blocking or blocked by it. Now, its controller no longer needs to assign an order, and simply divides its combat damage as they choose among all creatures it’s blocking or blocked by. See rules 510.1c-d.

\subsubsection*{Dash}
\addcontentsline{toc}{subsubsection}{Dash}

A keyword ability found on creature cards that allows them to be cast for an alternative cost. See rule 702.109, “Dash.”

\subsubsection*{Day}
\addcontentsline{toc}{subsubsection}{Day}

Along with night, a designation the game can have. See rule 730, “Day and Night,” and rule 702.145, “Daybound and Nightbound.”

\subsubsection*{Daybound}
\addcontentsline{toc}{subsubsection}{Daybound}

An ability found on the front faces of some double-faced cards. Cards with daybound and nightbound are face up when it’s day and face down when it’s night. See rule 702.145, “Daybound and Nightbound,” and rule 730, “Day and Night.”

\subsubsection*{Deal}
\addcontentsline{toc}{subsubsection}{Deal}

See Damage.

\subsubsection*{Deathtouch}
\addcontentsline{toc}{subsubsection}{Deathtouch}

A keyword ability that causes damage dealt by an object to be especially effective. See rule 702.2, “Deathtouch.”

\subsubsection*{Decayed}
\addcontentsline{toc}{subsubsection}{Decayed}

A keyword ability that means “This creature can’t block” and “When this creature attacks, sacrifice it at end of combat. See rule 702.147, “Decayed.”

\subsubsection*{Deck}
\addcontentsline{toc}{subsubsection}{Deck}

The collection of cards a player starts the game with; it becomes that player’s library. See rule 100, “General,” and rule 103, “Starting the Game.”

\subsubsection*{Declare Attackers}
\addcontentsline{toc}{subsubsection}{Declare Attackers}

To choose a set of creatures that will attack, declare whether each creature is attacking the defending player or a planeswalker that player controls, and pay any costs required to allow those creatures to attack. See rule 508.1.

\subsubsection*{Declare Attackers Step}
\addcontentsline{toc}{subsubsection}{Declare Attackers Step}

Part of the turn. This step is the second step of the combat phase. See rule 508, “Declare Attackers Step.”

\subsubsection*{Declare Blockers}
\addcontentsline{toc}{subsubsection}{Declare Blockers}

To choose a set of creatures that will block, declare which attacking creature each creature is blocking, and pay any costs required to allow those creatures to block. See rule 509.1.

\subsubsection*{Declare Blockers Step}
\addcontentsline{toc}{subsubsection}{Declare Blockers Step}

Part of the turn. This step is the third step of the combat phase. See rule 509, “Declare Blockers Step.”

\subsubsection*{Defender}
\addcontentsline{toc}{subsubsection}{Defender}

A keyword ability that prohibits a creature from attacking. See rule 702.3, “Defender.”

\subsubsection*{Defending Player}
\addcontentsline{toc}{subsubsection}{Defending Player}

The player who can be attacked, and whose planeswalkers can be attacked, during the combat phase. See rule 506.2. In certain multiplayer games, there may be more than one defending player; see rule 802, “Attack Multiple Players Option,” and rule 805.10.

\subsubsection*{Defending Team}
\addcontentsline{toc}{subsubsection}{Defending Team}

The team who can be attacked, and whose planeswalkers can be attacked, during the combat phase of a multiplayer game using the shared team turns option. See rule 805, “Shared Team Turns Option.”

\subsubsection*{Defense}
\addcontentsline{toc}{subsubsection}{Defense}

Part of a card that only battle cards have. A battle card’s defense is printed in its lower right corner. See rule 210, “Defense.”
A characteristic that only battles can have. See rule 310, “Battles.”

\subsubsection*{Delayed Triggered Ability}
\addcontentsline{toc}{subsubsection}{Delayed Triggered Ability}


An ability created by effects generated when some spells or abilities resolve, or when some replacement effects are applied, that does something later on rather than at that time. See rule 603.7.

\subsubsection*{Delve}
\addcontentsline{toc}{subsubsection}{Delve}

A keyword ability that lets you exile cards from your graveyard rather than pay generic mana to cast a spell. See rule 702.66, “Delve.”

\subsubsection*{Demonstrate}
\addcontentsline{toc}{subsubsection}{Demonstrate}

A triggered ability found on some spells that let its controller copy it and choose an opponent to also copy it. See rule 702.144, “Demonstrate.”

\subsubsection*{Dependency}
\addcontentsline{toc}{subsubsection}{Dependency}

A system that may be used to determine in which order continuous effects in the same layer or sublayer are applied. See rule 613.8. See also Timestamp Order.

\subsubsection*{Deploy Creatures Option}
\addcontentsline{toc}{subsubsection}{Deploy Creatures Option}

An option that may be used in certain multiplayer variants to pass control of creatures between teammates. See rule 804, “Deploy Creatures Option.”

\subsubsection*{Destroy}
\addcontentsline{toc}{subsubsection}{Destroy}

To move a permanent from the battlefield to its owner’s graveyard. See rule 701.8, “Destroy.”

\subsubsection*{Detain}
\addcontentsline{toc}{subsubsection}{Detain}

A keyword action that temporarily stops a permanent from attacking, blocking, or having its activated abilities activated. See rule 701.35, “Detain.”

\subsubsection*{Dethrone}
\addcontentsline{toc}{subsubsection}{Dethrone}

A keyword ability that puts a +1/+1 counter on a creature when it attacks the player with the most life. See rule 702.105, “Dethrone.”

\subsubsection*{Devoid}
\addcontentsline{toc}{subsubsection}{Devoid}

A characteristic-defining ability that makes an object colorless. See rule 702.114, “Devoid.”

\subsubsection*{Devotion}
\addcontentsline{toc}{subsubsection}{Devotion}

A numerical value a player has, equal to the number of mana symbols of a certain color among the mana costs of permanents that player controls. See rule 700.5.

\subsubsection*{Devour}
\addcontentsline{toc}{subsubsection}{Devour}

A keyword ability that can have a creature enter the battlefield with +1/+1 counters on it. See rule 702.82, “Devour.”

\subsubsection*{Dies}
\addcontentsline{toc}{subsubsection}{Dies}

A creature or planeswalker “dies” if it is put into a graveyard from the battlefield. See rule 700.4.

\subsubsection*{Discard}
\addcontentsline{toc}{subsubsection}{Discard}

To move a card from its owner’s hand to that player’s graveyard. See rule 701.9, “Discard.”

\subsubsection*{Discover}
\addcontentsline{toc}{subsubsection}{Discover}

A keyword ability that may allow a player to cast a random spell for free. See rule 701.57, “Discover.”

\subsubsection*{Disguise}
\addcontentsline{toc}{subsubsection}{Disguise}

A keyword ability that lets a card be cast face down as a 2/2 creature with ward {2. See rule 702.168, “Disguise,” and rule 708, “Face-Down Spells and Permanents.”

\subsubsection*{Disturb}
\addcontentsline{toc}{subsubsection}{Disturb}

A keyword ability that allows a player to cast a double-faced card transformed from the graveyard. See rule 702.146, “Disturb.”

\subsubsection*{Doctor’s Companion}
\addcontentsline{toc}{subsubsection}{Doctor’s Companion}

A partner ability that allows a player to play with two legendary creature cards as their commander if one of them has Doctor’s companion and the other is a Time Lord Doctor with no other creature types.

\subsubsection*{Door}
\addcontentsline{toc}{subsubsection}{Door}

A door is one half of a Room permanent. See rule 709, “Split Cards.”

\subsubsection*{Double}
\addcontentsline{toc}{subsubsection}{Double}

A keyword action used in a variety of contexts. See rule 701.10, “Double.”

\subsubsection*{Double Agenda}
\addcontentsline{toc}{subsubsection}{Double Agenda}

A variant of the hidden agenda ability. See rule 702.106, “Hidden Agenda.”

\subsubsection*{Double Strike}
\addcontentsline{toc}{subsubsection}{Double Strike}

A keyword ability that lets a creature deal its combat damage twice. See rule 702.4, “Double Strike.”

\subsubsection*{Double-Faced Cards}
\addcontentsline{toc}{subsubsection}{Double-Faced Cards}

Cards with two faces, one on each side of the card, and no Magic card back. See rule 712, “Double-Faced Cards.”

\subsubsection*{Draft}
\addcontentsline{toc}{subsubsection}{Draft}

A Limited format in which players choose cards one at a time from booster packs, then construct a deck solely from the chosen cards and basic land cards.
To choose a card during a draft and put it into your card pool.

\subsubsection*{Draft Round}
\addcontentsline{toc}{subsubsection}{Draft Round}

Part of a draft in which each player opens an unopened booster pack and the cards in those booster packs are drafted. See rules 905.1a and 905.1b.

\subsubsection*{Draw}
\addcontentsline{toc}{subsubsection}{Draw}

To put the top card of a player’s library into their hand as a turn-based action or as the result of an effect that uses the word “draw.” See rule 121, “Drawing a Card.”
The result of a game in which neither player wins or loses. See rule 104.4.

\subsubsection*{Draw Step}
\addcontentsline{toc}{subsubsection}{Draw Step}

Part of the turn. This step is the third and final step of the beginning phase. See rule 504, “Draw Step.”

\subsubsection*{Dredge}
\addcontentsline{toc}{subsubsection}{Dredge}

A keyword ability that lets a player return a card from their graveyard to their hand. See rule 702.52, “Dredge.”

\subsubsection*{Dungeon}
\addcontentsline{toc}{subsubsection}{Dungeon}

A card type found on nontraditional Magic cards. A dungeon card is not a permanent. See rule 309, “Dungeons.”

\subsubsection*{During (Obsolete)}
\addcontentsline{toc}{subsubsection}{During (Obsolete)}

Some older cards used the phrase “during [phase], [action].” These abilities were called “phase abilities.” In general, cards that were printed with phase abilities have received errata in the Oracle card reference so they have abilities that trigger at the beginning of a step or phase. “During” still appears in current card text, but only in its normal English sense and not as game terminology.

\subsubsection*{Earthbend}
\addcontentsline{toc}{subsubsection}{Earthbend}

A keyword action that causes a land to become a 0/0 creature with haste in addition to its other types and puts a number of +1/+1 counters on it. When that land dies or is put into exile, return it to the battlefield tapped under your control. See 701.66, “Earthbend.”

\subsubsection*{Echo}
\addcontentsline{toc}{subsubsection}{Echo}

A keyword ability that imposes a cost to keep a permanent on the battlefield. See rule 702.30, “Echo.”

\subsubsection*{EDH (Obsolete)}
\addcontentsline{toc}{subsubsection}{EDH (Obsolete)}

An older name for the Commander casual variant. See rule 903, “Commander.”

\subsubsection*{Effect}
\addcontentsline{toc}{subsubsection}{Effect}

Something that happens in the game as a result of a spell or ability. See rule 609, “Effects.”

\subsubsection*{Embalm}
\addcontentsline{toc}{subsubsection}{Embalm}

A keyword ability that lets a player exile a creature card from their graveyard to create a mummified token version of that card. See rule 702.128, “Embalm.”

\subsubsection*{Emblem}
\addcontentsline{toc}{subsubsection}{Emblem}

An emblem is a marker used to represent an object that has one or more abilities, but no other characteristics. See rule 114, “Emblems.”

\subsubsection*{Emerge}
\addcontentsline{toc}{subsubsection}{Emerge}

A keyword ability that lets a player cast a spell for less by sacrificing a creature. See rule 702.119, “Emerge.”

\subsubsection*{Emperor}
\addcontentsline{toc}{subsubsection}{Emperor}

The middle player on each team in an Emperor game. See rule 809, “Emperor Variant.”

\subsubsection*{Emperor Variant}
\addcontentsline{toc}{subsubsection}{Emperor Variant}

A multiplayer variant played among three-player teams. See rule 809, “Emperor Variant.”

\subsubsection*{Enchant}
\addcontentsline{toc}{subsubsection}{Enchant}

A keyword ability that defines what an Aura spell can target and what an Aura permanent can be attached to. See rule 303, “Enchantments,” and rule 702.5, “Enchant.”

\subsubsection*{Enchantment}
\addcontentsline{toc}{subsubsection}{Enchantment}

A card type. An enchantment is a permanent. See rule 303, “Enchantments.” See also Aura.

\subsubsection*{Enchantment Type}
\addcontentsline{toc}{subsubsection}{Enchantment Type}

A subtype that’s correlated to the enchantment card type. See rule 303, “Enchantments.” See rule 205.3h for the list of enchantment types.

\subsubsection*{Encoded}
\addcontentsline{toc}{subsubsection}{Encoded}

A term that describes the relationship between a permanent and a card exiled by a cipher ability. See rule 702.99, “Cipher.”

\subsubsection*{Encore}
\addcontentsline{toc}{subsubsection}{Encore}

A keyword ability that lets a player exile a creature card from their graveyard to, for each opponent, create a token that’s a copy of that card to attack that opponent. See rule 702.141, “Encore”

\subsubsection*{Encounter}
\addcontentsline{toc}{subsubsection}{Encounter}

To move a phenomenon card off the top of a planar deck and turn it face up. See rule 312, “Phenomena.”

\subsubsection*{End of Combat Step}
\addcontentsline{toc}{subsubsection}{End of Combat Step}

Part of the turn. This step is the fifth and final step of the combat phase. See rule 511, “End of Combat Step.”

\subsubsection*{End Step}
\addcontentsline{toc}{subsubsection}{End Step}

Part of the turn. This step is the first step of the ending phase. See rule 513, “End Step.”

\subsubsection*{End the Combat Phase}
\addcontentsline{toc}{subsubsection}{End the Combat Phase}

To “end the combat phase” as the result of an effect is to perform an expedited process that skips everything else that would happen that phase. See rule 723, “Ending Turns and Phases.”

\subsubsection*{End the Turn}
\addcontentsline{toc}{subsubsection}{End the Turn}

To “end the turn” as the result of an effect is to perform an expedited process that skips nearly everything else that would happen that turn. See rule 723, “Ending Turns and Phases.”

\subsubsection*{Ending Phase}
\addcontentsline{toc}{subsubsection}{Ending Phase}

Part of the turn. This phase is the fifth and final phase of the turn. See rule 512, “Ending Phase.”

\subsubsection*{Endure}
\addcontentsline{toc}{subsubsection}{Endure}

A keyword ability that lets you choose put +1/+1 counters on a creature or create a Spirit creature token. See rule 702.62, “Endure.”

\subsubsection*{Energy Symbol}
\addcontentsline{toc}{subsubsection}{Energy Symbol}

The energy symbol {E represents one energy counter. To pay {E, a player removes one energy counter from themselves.

\subsubsection*{Enlist}
\addcontentsline{toc}{subsubsection}{Enlist}

A keyword ability that allows a creature that could have attacked to support another creature. See rule 702.154, “Enlist.”

\subsubsection*{Enter}
\addcontentsline{toc}{subsubsection}{Enter}

In rules text, to enter the battlefield. See “Enters the Battlefield.”

\subsubsection*{Enters the Battlefield}
\addcontentsline{toc}{subsubsection}{Enters the Battlefield}

A nontoken permanent enters the battlefield when it’s moved onto the battlefield from another zone. A token enters the battlefield as it’s created. See rules 403.3, 603.6a, 603.6d, and 614.12. This phrase has been shortened to simply “enters” in rules text on cards in most contexts.

\subsubsection*{Entwine}
\addcontentsline{toc}{subsubsection}{Entwine}

A keyword ability that lets a player choose all modes for a spell rather than just the number specified. See rule 702.42, “Entwine.”

\subsubsection*{Epic}
\addcontentsline{toc}{subsubsection}{Epic}

A keyword ability that lets a player copy a spell at the beginning of each of their upkeeps at the expense of casting any other spells for the rest of the game. See rule 702.50, “Epic.”

\subsubsection*{Equip}
\addcontentsline{toc}{subsubsection}{Equip}

A keyword ability that lets a player attach an Equipment to a creature they control. See rule 301, “Artifacts,” and rule 702.6, “Equip.”

\subsubsection*{Equipment}
\addcontentsline{toc}{subsubsection}{Equipment}

An artifact subtype. Equipment can be attached to creatures. See rule 301, “Artifacts,” and rule 702.6, “Equip.”

\subsubsection*{Escalate}
\addcontentsline{toc}{subsubsection}{Escalate}

A keyword ability on some modal spells that adds a cost for choosing additional modes. See rule 702.120, “Escalate.”

\subsubsection*{Escape}
\addcontentsline{toc}{subsubsection}{Escape}

A keyword ability that lets a player cast a card from their graveyard. See rule 702.138, “Escape.”

\subsubsection*{Eternalize}
\addcontentsline{toc}{subsubsection}{Eternalize}

A keyword ability that lets a player exile a creature card from their graveyard to create an eternalized token version of that card. See rule 702.129, “Eternalize.”

\subsubsection*{Evasion Ability}
\addcontentsline{toc}{subsubsection}{Evasion Ability}

An ability that restricts what creatures can block an attacking creature. See rules 509.1b–c.

\subsubsection*{Event}
\addcontentsline{toc}{subsubsection}{Event}

Anything that happens in a game. See rule 700.1.

\subsubsection*{Evoke}
\addcontentsline{toc}{subsubsection}{Evoke}

A keyword ability that causes a permanent to be sacrificed when it enters the battlefield. See rule 702.74, “Evoke.”

\subsubsection*{Evolve}
\addcontentsline{toc}{subsubsection}{Evolve}

A keyword ability that lets you put a +1/+1 counter on a creature when a larger creature enters the battlefield under your control. See rule 702.100, “Evolve.”

\subsubsection*{Exalted}
\addcontentsline{toc}{subsubsection}{Exalted}

A keyword ability that can make a creature better in combat. See rule 702.83, “Exalted.”

\subsubsection*{Exchange}
\addcontentsline{toc}{subsubsection}{Exchange}

To swap two things, such as objects, sets of objects, or life totals. See rule 701.12, “Exchange.”

\subsubsection*{Exert}
\addcontentsline{toc}{subsubsection}{Exert}

A keyword action that stops a permanent from untapping during the next untap step of the player who exerted it. See rule 701.43, “Exert.”

\subsubsection*{Excess Damage}
\addcontentsline{toc}{subsubsection}{Excess Damage}

Damage dealt to a creature greater than what would be lethal damage or damage dealt to a planeswalker greater than its loyalty. See rule 120.4a.

\subsubsection*{Exile}
\addcontentsline{toc}{subsubsection}{Exile}

A zone. Exile is essentially a holding area for cards. It used to be known as the “removed-from-the-game” zone.
To put an object into the exile zone from whatever zone it’s currently in. An “exiled” card is one that’s been put into the exile zone.
See rule 406, “Exile.”

\subsubsection*{Exhaust}
\addcontentsline{toc}{subsubsection}{Exhaust}

A special kind of activated ability that may be activated only once. See rule 702.177, “Exhaust.”

\subsubsection*{Expansion Symbol}
\addcontentsline{toc}{subsubsection}{Expansion Symbol}

A card’s expansion symbol is a small icon normally printed below the right edge of the illustration that has no effect on game play. See rule 206, “Expansion Symbol.”

\subsubsection*{Expend}
\addcontentsline{toc}{subsubsection}{Expend}

A word found on some abilities that care how much mana a player has spent to cast spells this turn. See rule 700.14.

\subsubsection*{Exploit}
\addcontentsline{toc}{subsubsection}{Exploit}

A keyword ability that lets you sacrifice a creature for a benefit. See rule 702.110, “Exploit.”

\subsubsection*{Explore}
\addcontentsline{toc}{subsubsection}{Explore}

A keyword action that causes a player to reveal the top card of their library and then to take different actions depending on whether a land card is revealed this way. See rule 701.44, “Explore.”

\subsubsection*{Extort}
\addcontentsline{toc}{subsubsection}{Extort}

A keyword ability that lets you gain life and have opponents lose life whenever you cast a spell. See rule 702.101, “Extort.”

\subsubsection*{Extra Turn}
\addcontentsline{toc}{subsubsection}{Extra Turn}

A turn created by an effect of a spell or ability. See rule 500.7. For rules about extra turns in a multiplayer game using the shared team turns option, see 805.8. For rules about extra turns in a Grand Melee game, see rule 807.4.

\subsubsection*{Fabricate}
\addcontentsline{toc}{subsubsection}{Fabricate}

A keyword ability that lets you choose whether to create Servo tokens or put +1/+1 counters on a creature. See rule 702.123, “Fabricate.”

\subsubsection*{Face a Villainous Choice}
\addcontentsline{toc}{subsubsection}{Face a Villainous Choice}

A keyword action that causes a player to choose one of two listed choices. See rule 701.55, “Face a Villainous Choice.”

\subsubsection*{Face Down}
\addcontentsline{toc}{subsubsection}{Face Down}

A card is “face down” if it’s physically positioned so the card back is showing. Cards in some zones are normally kept face down. See section 4, “Zones.”
A status a permanent may have. See rule 110.5 and rule 702.37, “Morph.”
Face-down spells have additional rules. See rule 708, “Face-Down Spells and Permanents,” and rule 702.37, “Morph.”

\subsubsection*{Face Up}
\addcontentsline{toc}{subsubsection}{Face Up}

A card is “face up” if it’s physically positioned so the card front is showing. Cards in some zones are normally kept face up. See section 4, “Zones.”
A default status a permanent may have. See rule 110.5 and rule 702.37, “Morph.”

\subsubsection*{Fading}
\addcontentsline{toc}{subsubsection}{Fading}

A keyword ability that limits how long a permanent remains on the battlefield. See rule 702.32, “Fading.”

\subsubsection*{Fateseal}
\addcontentsline{toc}{subsubsection}{Fateseal}

To manipulate some of the cards on top of an opponent’s library. See rule 701.29, “Fateseal.”

\subsubsection*{Fear}
\addcontentsline{toc}{subsubsection}{Fear}

A keyword ability that restricts how a creature may be blocked. See rule 702.36, “Fear.”

\subsubsection*{Fight}
\addcontentsline{toc}{subsubsection}{Fight}

When two creatures fight, each deals damage equal to its power to the other. See rule 701.14, “Fight.”

\subsubsection*{Finality Counter}
\addcontentsline{toc}{subsubsection}{Finality Counter}

A counter that exiles the permanent it is on if that permanent would go to the graveyard from the battlefield. See rule 122.1h.

\subsubsection*{Firebending}
\addcontentsline{toc}{subsubsection}{Firebending}

A keyword ability that adds red mana until end of combat whenever a creature with that ability attacks. See rule 702.189, “Firebending.”

\subsubsection*{First Strike}
\addcontentsline{toc}{subsubsection}{First Strike}

A keyword ability that lets a creature deal its combat damage before other creatures. See rule 702.7, “First Strike.”

\subsubsection*{Flanking}
\addcontentsline{toc}{subsubsection}{Flanking}

A keyword ability that can make a creature better in combat. See rule 702.25, “Flanking.”

\subsubsection*{Flash}
\addcontentsline{toc}{subsubsection}{Flash}

A keyword ability that lets a player play a card any time they could cast an instant. See rule 702.8, “Flash.”

\subsubsection*{Flashback}
\addcontentsline{toc}{subsubsection}{Flashback}

A keyword ability that lets a player cast a card from their graveyard. See rule 702.34, “Flashback.”

\subsubsection*{Flavor Text}
\addcontentsline{toc}{subsubsection}{Flavor Text}

Text in italics (but not in parentheses) in the text box of a card that has no effect on play. See rule 207.2.

\subsubsection*{Flavor Word}
\addcontentsline{toc}{subsubsection}{Flavor Word}

An italicized word with no rules meaning that provides a flavorful description of an ability. See rule 207.2d.

\subsubsection*{Flip Cards}
\addcontentsline{toc}{subsubsection}{Flip Cards}

Cards with a two-part card frame (one part of which is printed upside down) on a single card. See rule 710, “Flip Cards.”

\subsubsection*{Flipped}
\addcontentsline{toc}{subsubsection}{Flipped}

A status a permanent may have. See rule 110.5 and rule 710, “Flip Cards.” See also Unflipped.

\subsubsection*{Flipping a Coin}
\addcontentsline{toc}{subsubsection}{Flipping a Coin}

A method of randomization with two possible outcomes of equal likelihood. See rule 705, “Flipping a Coin.”

\subsubsection*{Flying}
\addcontentsline{toc}{subsubsection}{Flying}

A keyword ability that restricts how a creature may be blocked. See rule 702.9, “Flying.”

\subsubsection*{Food Token}
\addcontentsline{toc}{subsubsection}{Food Token}

A Food token is a colorless artifact token with “{2, {T, Sacrifice this token: You gain 3 life.” For more information about predefined tokens, see rule 111.10.

\subsubsection*{For Mirrodin!}
\addcontentsline{toc}{subsubsection}{For Mirrodin!}

A keyword ability that creates a 2/2 red Rebel creature token and then attaches the Equipment with the ability to that token. See rule 702.163, “For Mirrodin!”

\subsubsection*{Forage}
\addcontentsline{toc}{subsubsection}{Forage}

To pay a cost of exiling three cards from your graveyard or sacrificing a Food. See rule 701.61, “Forage.”

\subsubsection*{Forecast}
\addcontentsline{toc}{subsubsection}{Forecast}

A keyword ability that allows an activated ability to be activated from a player’s hand. See rule 702.57, “Forecast.”

\subsubsection*{Forest}
\addcontentsline{toc}{subsubsection}{Forest}

One of the five basic land types. Any land with this subtype has the ability “{T: Add {G.” See rule 305.6.

\subsubsection*{Forestcycling}
\addcontentsline{toc}{subsubsection}{Forestcycling}

See Typecycling.

\subsubsection*{Forestwalk}
\addcontentsline{toc}{subsubsection}{Forestwalk}

See Landwalk.

\subsubsection*{Foretell}
\addcontentsline{toc}{subsubsection}{Foretell}

A keyword ability that lets a player exile cards from their hand and cast them for an alternative cost on future turns. See rule 702.143, “Foretell.”

\subsubsection*{Foretold}
\addcontentsline{toc}{subsubsection}{Foretold}

A card exiled using the foretell special action becomes foretold. Other effects can also make an exiled card foretold. A spell was foretold if it was a foretold card in exile before it was cast.

\subsubsection*{Fortification}
\addcontentsline{toc}{subsubsection}{Fortification}

An artifact subtype. Fortifications can be attached to lands. See rule 301, “Artifacts,” and rule 702.67, “Fortify.”

\subsubsection*{Fortify}
\addcontentsline{toc}{subsubsection}{Fortify}

A keyword ability that lets a player attach a Fortification to a land they control. See rule 301, “Artifacts,” and rule 702.67, “Fortify.”

\subsubsection*{Frenzy}
\addcontentsline{toc}{subsubsection}{Frenzy}

A keyword ability that can make a creature better in combat. See rule 702.68, “Frenzy.”

\subsubsection*{Free-for-All}
\addcontentsline{toc}{subsubsection}{Free-for-All}

A multiplayer variant in which a group of players compete as individuals against each other. See rule 806, “Free-for-All Variant.”

\subsubsection*{Freerunning}
\addcontentsline{toc}{subsubsection}{Freerunning}

A keyword ability that allows certain spells to be cast for an alternative cost. See rule 702.173, “Freerunning.”

\subsubsection*{Full Party}
\addcontentsline{toc}{subsubsection}{Full Party}

A player has a full party if the number of creatures in their party is four. See rule 700.8.

\subsubsection*{Fuse}
\addcontentsline{toc}{subsubsection}{Fuse}

A keyword ability that allows a player to cast both halves of a split card. See rule 702.102, “Fuse.”

\subsubsection*{Fused Split Spell}
\addcontentsline{toc}{subsubsection}{Fused Split Spell}

A split card on the stack that has been cast using the fuse ability or a copy of such a card. See rule 702.102, “Fuse.”

\subsubsection*{General}
\addcontentsline{toc}{subsubsection}{General}

Any player in the Emperor multiplayer variant who isn’t an emperor. See rule 809, “Emperor Variant.”

\subsubsection*{Generic Mana}
\addcontentsline{toc}{subsubsection}{Generic Mana}

Mana in a cost represented by numerical symbols (such as {1) or variable symbols (such as {X) that can be paid with mana of any type. See rule 107.4.

\subsubsection*{Gift}
\addcontentsline{toc}{subsubsection}{Gift}

A keyword ability that allows a spell’s caster to choose an opponent as to receive a benefit as the spell resolves or when the permanent with the ability enters. See rule 702.174, “Gift.”

\subsubsection*{Global Enchantment (Obsolete)}
\addcontentsline{toc}{subsubsection}{Global Enchantment (Obsolete)}

An obsolete term for a non-Aura enchantment. Cards printed with this text have received errata in the Oracle card reference.

\subsubsection*{Goad}
\addcontentsline{toc}{subsubsection}{Goad}

A keyword action that causes a creature to be goaded until a player’s next turn. See rule 701.15, “Goad.”

\subsubsection*{Goaded}
\addcontentsline{toc}{subsubsection}{Goaded}

A designation a permanent can have. Goaded creatures are forced to attack and to attack a player other than the player that caused it to be goaded. See rule 701.15, “Goad.”

\subsubsection*{Gold Token}
\addcontentsline{toc}{subsubsection}{Gold Token}

A Gold token is a colorless artifact token with “Sacrifice this token: Add one mana of any color.” For more information on predefined tokens, see rule 111.10.

\subsubsection*{Graft}
\addcontentsline{toc}{subsubsection}{Graft}

A keyword ability that has a permanent enter the battlefield with +1/+1 counters on it and can move those counters to other creatures. See rule 702.58, “Graft.”

\subsubsection*{Grand Melee}
\addcontentsline{toc}{subsubsection}{Grand Melee}

A multiplayer variant in which a large group of players (usually ten or more) compete as individuals against each other. See rule 807, “Grand Melee Variant.”

\subsubsection*{Gravestorm}
\addcontentsline{toc}{subsubsection}{Gravestorm}

A keyword ability that creates copies of a spell. See rule 702.69, “Gravestorm.”

\subsubsection*{Graveyard}
\addcontentsline{toc}{subsubsection}{Graveyard}

A zone. A player’s graveyard is their discard pile.
All the cards in a player’s graveyard.
See rule 404, “Graveyard.”

\subsubsection*{Hand}
\addcontentsline{toc}{subsubsection}{Hand}

A zone. A player’s hand is where that player holds cards they have drawn but not played yet.
All the cards in a player’s hand.
See rule 402, “Hand.”

\subsubsection*{Hand Modifier}
\addcontentsline{toc}{subsubsection}{Hand Modifier}

A characteristic that only vanguards have. See rule 211, “Hand Modifier.”

\subsubsection*{Harmonize}
\addcontentsline{toc}{subsubsection}{Harmonize}

A keyword ability that lets a player cast a card from their graveyard for a specific cost and lets them tap a creature they control to reduce that cost. See rule 702.180, “Harmonize.”

\subsubsection*{Harness}
\addcontentsline{toc}{subsubsection}{Harness}

A keyword action that grants a permanent the harnessed designation. See rule 701.64, “Harness.”

\subsubsection*{Harnessed}
\addcontentsline{toc}{subsubsection}{Harnessed}

A designation permanents can have. Infinity permanents have their ∞ abilities as long as they are harnessed. See rule 701.64, “Harness,” and rule 702.186, “∞ (Infinity).”

\subsubsection*{Haste}
\addcontentsline{toc}{subsubsection}{Haste}

A keyword ability that lets a creature ignore the “summoning sickness” rule. See rule 702.10, “Haste,” and rule 302.6.

\subsubsection*{Haunt}
\addcontentsline{toc}{subsubsection}{Haunt}

A keyword ability that exiles cards. A card exiled this way “haunts” a creature targeted by the haunt ability. See rule 702.55, “Haunt.”

\subsubsection*{Hexproof}
\addcontentsline{toc}{subsubsection}{Hexproof}

A keyword ability that precludes a permanent or player from being targeted by an opponent. See rule 702.11, “Hexproof.”

\subsubsection*{Hidden Agenda}
\addcontentsline{toc}{subsubsection}{Hidden Agenda}

A keyword ability that allows a conspiracy card to be put into the command zone face down. See rule 702.106, “Hidden Agenda.”

\subsubsection*{Hidden Zone}
\addcontentsline{toc}{subsubsection}{Hidden Zone}

A zone in which not all players can be expected to see the cards’ faces. See rule 400.2. See also Public Zone.

\subsubsection*{Hideaway}
\addcontentsline{toc}{subsubsection}{Hideaway}

A keyword ability that lets a player store a secret card. See rule 702.75, “Hideaway.”

\subsubsection*{Historic}
\addcontentsline{toc}{subsubsection}{Historic}

An object is historic if it has the legendary supertype, the artifact card type, or the Saga subtype. See rule 700.6.

\subsubsection*{Horsemanship}
\addcontentsline{toc}{subsubsection}{Horsemanship}

A keyword ability that restricts how a creature may be blocked. See rule 702.31, “Horsemanship.”

\subsubsection*{Hybrid Card}
\addcontentsline{toc}{subsubsection}{Hybrid Card}

A card with one or more hybrid mana symbols in its mana cost. See rule 202.2f.

\subsubsection*{Hybrid Mana Symbols}
\addcontentsline{toc}{subsubsection}{Hybrid Mana Symbols}

A mana symbol that represents a cost that can be paid in one of two ways. See rule 107.4.

\subsubsection*{Hybrid Phyrexian Mana Symbols}
\addcontentsline{toc}{subsubsection}{Hybrid Phyrexian Mana Symbols}

A mana symbol that represents a cost that can be paid in one of three ways. See rule 107.4.

\subsubsection*{Job Select}
\addcontentsline{toc}{subsubsection}{Job Select}

A keyword ability that creates a 1/1 colorless Hero creature token and then attaches the Equipment with the ability to that token. See rule 702.182, “Job Select.”

\subsubsection*{Junk Token}
\addcontentsline{toc}{subsubsection}{Junk Token}

A Junk token is a colorless artifact token with {T, Sacrifice this token: Exile the top card of your library. You may play that card this turn. Activate only as a sorcery.” For more information about predefined tokens, see rule 111.10.

\subsubsection*{If}
\addcontentsline{toc}{subsubsection}{If}

See Intervening “If” Clause.

\subsubsection*{Illegal Action}
\addcontentsline{toc}{subsubsection}{Illegal Action}

An action that violates the rules of the game and/or requirements or restrictions created by effects. See rule 732, “Handling Illegal Actions.”

\subsubsection*{Illegal Target}
\addcontentsline{toc}{subsubsection}{Illegal Target}

A target that no longer exists or no longer meets the specifications stated by the spell or ability that’s targeting it. See rule 608.2b.

\subsubsection*{Illustration}
\addcontentsline{toc}{subsubsection}{Illustration}

A picture printed on the upper half of a card that has no effect on game play. See rule 203, “Illustration.”

\subsubsection*{Illustration Credit}
\addcontentsline{toc}{subsubsection}{Illustration Credit}

Information printed directly below the text box that has no effect on game play. See rule 213, “Information Below the Text Box.”

\subsubsection*{Impending}
\addcontentsline{toc}{subsubsection}{Impending}

An ability on some creatures that allows them to be cast for an alternative cost. If cast for its impending cost, it isn’t a creature for some period of time. See rule 702.176, “Impending.”

\subsubsection*{Imprint}
\addcontentsline{toc}{subsubsection}{Imprint}

“Imprint” used to be a keyword ability. It is now an ability word and has no rules meaning. All cards printed with the imprint keyword have received errata in the Oracle card reference.

\subsubsection*{Improvise}
\addcontentsline{toc}{subsubsection}{Improvise}

A keyword ability that lets you tap artifacts rather than pay mana to cast a spell. See rule 702.126, “Improvise.”

\subsubsection*{In Play (Obsolete)}
\addcontentsline{toc}{subsubsection}{In Play (Obsolete)}

An obsolete term for the battlefield. Cards that were printed with text that contain the phrases “in play,” “from play,” “into play,” or the like are referring to the battlefield and have received errata in the Oracle card reference. See Battlefield.

\subsubsection*{In Response To}
\addcontentsline{toc}{subsubsection}{In Response To}

An instant spell that’s been cast, or an activated ability that’s been activated, while another spell or ability is on the stack has been cast or activated “in response to” the earlier spell or ability. See rule 117.7.

\subsubsection*{Incubate}
\addcontentsline{toc}{subsubsection}{Incubate}

A keyword action that creates an Incubator token with a specified number of +1/+1 counters on it. See rule 701.53, “Incubate.”

\subsubsection*{Incubator Token}
\addcontentsline{toc}{subsubsection}{Incubator Token}

An Incubator token is a double-faced token. Its front face is a colorless Incubator artifact with “{2: Transform this token.” Its back face is a 0/0 colorless Phyrexian artifact creature named “Phyrexian Token.” For more information about predefined tokens, see rule 111.10.

\subsubsection*{Independent}
\addcontentsline{toc}{subsubsection}{Independent}

See Dependency.

\subsubsection*{Indestructible}
\addcontentsline{toc}{subsubsection}{Indestructible}

A keyword ability that precludes a permanent from being destroyed. See rule 702.12.

\subsubsection*{Infect}
\addcontentsline{toc}{subsubsection}{Infect}

A keyword ability that affects how an object deals damage to creatures and players. See rule 702.90, “Infect.”

\subsubsection*{Infinity}
\addcontentsline{toc}{subsubsection}{Infinity}

An artifact subtype.
2. ∞ is a keyword found on Infinity cards that grants an ability as long as that permanent is harnessed. See rule 702.186, “∞ (Infinity),” and rule 701.64, “Harness.”

\subsubsection*{Ingest}
\addcontentsline{toc}{subsubsection}{Ingest}

A keyword ability that can exile the top card of a player’s library. See rule 702.115, “Ingest.”

\subsubsection*{Initiative}
\addcontentsline{toc}{subsubsection}{Initiative}

A designation a player can have. Some effects instruct a player to take the initiative. The player with the initiative ventures into Undercity whenever they take the initiative and at the beginning of their upkeep. See rule 725, “The Initiative.”

\subsubsection*{Instant}
\addcontentsline{toc}{subsubsection}{Instant}

A card type. An instant is not a permanent. See rule 304, “Instants.”

\subsubsection*{Instead}
\addcontentsline{toc}{subsubsection}{Instead}

Effects that use the word “instead” are replacement effects. The word “instead” indicates what an event will be replaced with. See rule 614, “Replacement Effects.”

\subsubsection*{Interrupt (Obsolete)}
\addcontentsline{toc}{subsubsection}{Interrupt (Obsolete)}

An obsolete card type. All cards printed with this card type are now instants. All abilities that, as printed, said a player could “play as an interrupt” can now be activated like any other activated abilities (unless they’re mana abilities, in which case they follow those rules instead). All relevant cards have been given errata in the Oracle card reference.

\subsubsection*{Intervening “If” Clause}
\addcontentsline{toc}{subsubsection}{Intervening “If” Clause}

A specially worded condition checked as a triggered ability would trigger and again as it would resolve. See rule 603.4.

\subsubsection*{Intimidate}
\addcontentsline{toc}{subsubsection}{Intimidate}

A keyword ability that restricts how a creature may be blocked. See rule 702.13, “Intimidate.”

\subsubsection*{Investigate}
\addcontentsline{toc}{subsubsection}{Investigate}

A keyword action that creates a Clue artifact token. See rule 701.16, “Investigate.”

\subsubsection*{Island}
\addcontentsline{toc}{subsubsection}{Island}

One of the five basic land types. Any land with this subtype has the ability “{T: Add {U.” See rule 305.6.

\subsubsection*{Islandcycling}
\addcontentsline{toc}{subsubsection}{Islandcycling}

See Typecycling.

\subsubsection*{Islandhome (Obsolete)}
\addcontentsline{toc}{subsubsection}{Islandhome (Obsolete)}

An obsolete keyword ability that meant “This creature can’t attack unless defending player controls an Island” and “When you control no Islands, sacrifice this creature.” Cards printed with this ability have been given errata in the Oracle card reference.

\subsubsection*{Islandwalk}
\addcontentsline{toc}{subsubsection}{Islandwalk}

See Landwalk.

\subsubsection*{Jump-Start}
\addcontentsline{toc}{subsubsection}{Jump-Start}

A keyword ability that lets a player cast a card from their graveyard by discarding a card. See rule 702.133, “Jump-Start.”

\subsubsection*{Keyword Ability}
\addcontentsline{toc}{subsubsection}{Keyword Ability}

A game term, such as “flying” or “haste,” used as shorthand for a longer ability or group of abilities. See rule 702, “Keyword Abilities.”

\subsubsection*{Keyword Action}
\addcontentsline{toc}{subsubsection}{Keyword Action}

A verb, such as “destroy” or “cast,” used as a game term rather than as its normal English meaning. See rule 701, “Keyword Actions.”

\subsubsection*{Keyword Counter}
\addcontentsline{toc}{subsubsection}{Keyword Counter}

A marker placed on an object that modifies its characteristics by granting it a keyword. See rule 122, “Counters.”

\subsubsection*{Kicker, Kicked}
\addcontentsline{toc}{subsubsection}{Kicker, Kicked}

Kicker is a keyword ability that represents an optional additional cost. A spell has been kicked if its controller declared the intention to pay any or all of its kicker costs. See rule 702.33, “Kicker.”

\subsubsection*{Kindred}
\addcontentsline{toc}{subsubsection}{Kindred}

A card type. Whether or not a kindred is a permanent depends on its other card type. See rule 308, “Kindreds.”

\subsubsection*{Land}
\addcontentsline{toc}{subsubsection}{Land}

A card type. A land is a permanent. See rule 305, “Lands.”

\subsubsection*{Land Type}
\addcontentsline{toc}{subsubsection}{Land Type}

A subtype that’s correlated to the land card type. See rule 305, “Lands.” See rule 205.3i for the list of land types.

\subsubsection*{Lander Token}
\addcontentsline{toc}{subsubsection}{Lander Token}

A Lander token is a colorless artifact token with “{2, {T, Sacrifice this token: Search your library for a basic land card, put it onto the battlefield tapped, then shuffle.” For more information about predefined tokens, see rule 111.10.

\subsubsection*{Landwalk}
\addcontentsline{toc}{subsubsection}{Landwalk}

A generic term for a group of keyword abilities that restrict whether a creature may be blocked. See rule 702.14, “Landwalk.”

\subsubsection*{Last Known Information}
\addcontentsline{toc}{subsubsection}{Last Known Information}

Information about an object that’s no longer in the zone it’s expected to be in, or information about a player who’s no longer in the game. This information captures that object’s last existence in that zone or that player’s last existence in the game. See rules 113.7a, 608.2b, 608.2h, and 800.4h.

\subsubsection*{Layer}
\addcontentsline{toc}{subsubsection}{Layer}

A system used to determine in which order continuous effects are applied. See rule 613, “Interaction of Continuous Effects.” See also Dependency, Timestamp Order.

\subsubsection*{Learn}
\addcontentsline{toc}{subsubsection}{Learn}

A keyword action that lets a player add a Lesson card to their hand from outside the game or discard a card to draw a card. See rule 701.48, “Learn.”

\subsubsection*{Leaves the Battlefield}
\addcontentsline{toc}{subsubsection}{Leaves the Battlefield}

A permanent “leaves the battlefield” when it’s moved from the battlefield to another zone, or (if it’s phased in) when it leaves the game because its owner leaves the game. See rules 603.6c and 603.10.

\subsubsection*{Legal Text}
\addcontentsline{toc}{subsubsection}{Legal Text}

Information printed directly below the text box that has no effect on game play. See rule 213, “Information Below the Text Box.”

\subsubsection*{Legend (Obsolete)}
\addcontentsline{toc}{subsubsection}{Legend (Obsolete)}

An obsolete creature type. Cards printed with this subtype have been given errata in the Oracle card reference so they have the legendary supertype instead. See Legendary.

\subsubsection*{Legendary}
\addcontentsline{toc}{subsubsection}{Legendary}

A supertype that’s normally relevant on permanents. See rule 205.4, “Supertypes.” See also Legend Rule.

\subsubsection*{Legend Rule}
\addcontentsline{toc}{subsubsection}{Legend Rule}

A state-based action that causes a player who controls two or more legendary permanents with the same name to put all but one into their owners’ graveyards. See rule 704.5j.

\subsubsection*{Lethal Damage}
\addcontentsline{toc}{subsubsection}{Lethal Damage}

An amount of damage greater than or equal to a creature’s toughness. See rules 120.4a, 120.6, 510.1, and 704.5g.

\subsubsection*{Level}
\addcontentsline{toc}{subsubsection}{Level}

A numerical designation a permanent may have. A Class enchantment’s level determines what other abilities it has. See rule 716, “Class Cards.”

\subsubsection*{Level Symbol}
\addcontentsline{toc}{subsubsection}{Level Symbol}

A symbol that represents a keyword ability indicating abilities, power, and toughness a leveler card may have. See rule 107.8 and rule 711, “Leveler Cards.”

\subsubsection*{Level Up}
\addcontentsline{toc}{subsubsection}{Level Up}

A keyword ability that can put level counters on a creature. See rule 702.87, “Level Up.” For class level abilities of Class cards, see rule 716, “Class Cards.”

\subsubsection*{Leveler Cards}
\addcontentsline{toc}{subsubsection}{Leveler Cards}

Cards with striated text boxes and three power/toughness boxes. See rule 711, “Leveler Cards.”

\subsubsection*{Library}
\addcontentsline{toc}{subsubsection}{Library}

A zone. A player’s library is where that player draws cards from.
All the cards in a player’s library.
See rule 401, “Library.”

\subsubsection*{Life, Life Total}
\addcontentsline{toc}{subsubsection}{Life, Life Total}

Each player has an amount of “life,” represented by that player’s “life total.” Life may be gained or lost. See rule 119, “Life.”

\subsubsection*{Life Modifier}
\addcontentsline{toc}{subsubsection}{Life Modifier}

A characteristic that only vanguards have. See rule 212, “Life Modifier.”

\subsubsection*{Lifelink}
\addcontentsline{toc}{subsubsection}{Lifelink}

A keyword ability that causes a player to gain life. See rule 702.15, “Lifelink.”

\subsubsection*{Limited}
\addcontentsline{toc}{subsubsection}{Limited}

A way of playing in which each player gets a quantity of unopened Magic product and creates their own deck on the spot. See rule 100.2.

\subsubsection*{Limited Range of Influence}
\addcontentsline{toc}{subsubsection}{Limited Range of Influence}

An optional rule used in some multiplayer games that limits what a player can affect. See rule 801, “Limited Range of Influence Option.”

\subsubsection*{Linked Abilities}
\addcontentsline{toc}{subsubsection}{Linked Abilities}

Two abilities printed on the same object such that one of them causes actions to be taken or objects to be affected and the other one directly refers to those actions or objects. See rule 607, “Linked Abilities.”

\subsubsection*{Living Metal}
\addcontentsline{toc}{subsubsection}{Living Metal}

A keyword ability found on some Vehicles that turns them into a creature during your turn. See rule 702.161, “Living Metal.”

\subsubsection*{Living Weapon}
\addcontentsline{toc}{subsubsection}{Living Weapon}

A keyword ability that creates a 0/0 black Phyrexian Germ creature token and then attaches the Equipment with the ability to that token. See rule 702.92, “Living Weapon.”

\subsubsection*{Local Enchantment (Obsolete)}
\addcontentsline{toc}{subsubsection}{Local Enchantment (Obsolete)}

An obsolete term for an Aura. Cards printed with this text have received errata in the Oracle card reference.

\subsubsection*{Lock}
\addcontentsline{toc}{subsubsection}{Lock}

To remove an unlocked designation from a permanent that has one or more unlocked halves. See rule 709.5g.

\subsubsection*{Locked}
\addcontentsline{toc}{subsubsection}{Locked}

One half of a split permanent is “locked” if it doesn’t have the appropriate unlocked designation. See rule 709.5.

\subsubsection*{London Mulligan}
\addcontentsline{toc}{subsubsection}{London Mulligan}

Informal term for the current system of mulligan rules. See rule 103.5.

\subsubsection*{Loop}
\addcontentsline{toc}{subsubsection}{Loop}

A set of actions that could be repeated indefinitely. See rule 731, “Taking Shortcuts.”

\subsubsection*{Lose the Game}
\addcontentsline{toc}{subsubsection}{Lose the Game}

There are several ways to lose the game. See rule 104, “Ending the Game,” rule 810.8 (for additional rules for Two-Headed Giant games), rule 809.5 (for additional rules for Emperor games), and rule 903.10 (for an additional rule for Commander games).

\subsubsection*{Loyalty}
\addcontentsline{toc}{subsubsection}{Loyalty}

Part of a card that only planeswalker cards have. A planeswalker card’s loyalty is printed in its lower right corner. See rule 209, “Loyalty.”
A characteristic that only planeswalkers have. See rule 306.5.

\subsubsection*{Loyalty Ability}
\addcontentsline{toc}{subsubsection}{Loyalty Ability}

An activated ability with a loyalty symbol in its cost. See rule 606, “Loyalty Abilities.”

\subsubsection*{Madness}
\addcontentsline{toc}{subsubsection}{Madness}

A keyword ability that lets a player cast a card they discard. See rule 702.35, “Madness.”

\subsubsection*{Main Game}
\addcontentsline{toc}{subsubsection}{Main Game}

The game in which a spell (or ability) that created a subgame was cast (or activated). See rule 728, “Subgames.”

\subsubsection*{Main Phase}
\addcontentsline{toc}{subsubsection}{Main Phase}

Part of the turn. The first, or precombat, main phase is the second phase of the turn. The second, or postcombat, main phase is the fourth phase of the turn. See rule 505, “Main Phase.”

\subsubsection*{Mana}
\addcontentsline{toc}{subsubsection}{Mana}

The primary resource in the game. It is spent to pay costs, usually when casting spells and activating abilities. See rule 106, “Mana,” rule 107.4, and rule 202, “Mana Cost and Color.”

\subsubsection*{Mana Ability}
\addcontentsline{toc}{subsubsection}{Mana Ability}

An activated or triggered ability that could create mana and doesn’t use the stack. See rule 605, “Mana Abilities.”

\subsubsection*{Mana Burn (Obsolete)}
\addcontentsline{toc}{subsubsection}{Mana Burn (Obsolete)}

Older versions of the rules stated that unspent mana caused a player to lose life; this was called “mana burn.” That rule no longer exists.

\subsubsection*{Mana Cost}
\addcontentsline{toc}{subsubsection}{Mana Cost}

A characteristic, and part of a card. A card’s mana cost is indicated by the mana symbols printed in its upper right corner. See rule 107.4 and rule 202, “Mana Cost and Color.”

\subsubsection*{Mana Pool}
\addcontentsline{toc}{subsubsection}{Mana Pool}

Where mana created by an effect is temporarily stored. See rule 106.4.

\subsubsection*{Mana Source (Obsolete)}
\addcontentsline{toc}{subsubsection}{Mana Source (Obsolete)}

An obsolete card type. All cards printed with this card type are now instants. All abilities that, as printed, said a player could “play as a mana source” are now mana abilities. All relevant cards have been given errata in the Oracle card reference.

\subsubsection*{Mana Symbol}
\addcontentsline{toc}{subsubsection}{Mana Symbol}

An icon that represents mana or a mana cost. See rule 107.4.

\subsubsection*{Mana Value}
\addcontentsline{toc}{subsubsection}{Mana Value}

The total amount of mana in a mana cost, regardless of color. See rule 202.3.

\subsubsection*{Manifest}
\addcontentsline{toc}{subsubsection}{Manifest}

A keyword action that puts a card onto the battlefield face down as a 2/2 creature. See rule 701.40, “Manifest,” and rule 708, “Face-Down Spells and Permanents.”

\subsubsection*{Manifest Dread}
\addcontentsline{toc}{subsubsection}{Manifest Dread}

A keyword action that puts one of the top two cards of your library onto the battlefield face down as a 2/2 creature. See rule 701.62, “Manifest Dread,” rule 701.40, “Manifest,” and rule 708, “Face-Down Spells and Permanents.”

\subsubsection*{Map}
\addcontentsline{toc}{subsubsection}{Map}

A Map token is a colorless Map artifact token with “{1, {T, Sacrifice this token: Target creature you control explores. Activate only as a sorcery.” See rule 701.44, “Explore.” For more information about predefined tokens, see rule 110.10.

\subsubsection*{Match}
\addcontentsline{toc}{subsubsection}{Match}

A multiplayer game or a two-player series of games (usually best-two-of-three) played in a tournament. See rule 100.6.

\subsubsection*{Max Speed}
\addcontentsline{toc}{subsubsection}{Max Speed}

A player has max speed if their speed is 4. See rule 702.179, “Start Your Engines!”
A keyword ability that grants an ability to the permanent or card it’s on only if that permanent’s controller (or that card’s owner, if it isn’t on the battlefield) has a speed of 4. See rule 702.178, “Max Speed.”

\subsubsection*{Maximum Hand Size}
\addcontentsline{toc}{subsubsection}{Maximum Hand Size}

The number of cards in hand a player must discard down to during their cleanup step. See rule 402.2 and 514.1.

\subsubsection*{Mayhem}
\addcontentsline{toc}{subsubsection}{Mayhem}

A keyword ability that allows you to play cards you discarded this turn from your graveyard for an alternative cost. See rule 702.187, “Mayhem.”

\subsubsection*{Megamorph}
\addcontentsline{toc}{subsubsection}{Megamorph}

A variant of the morph ability that puts a +1/+1 counter on the creature as it turns face up. See rule 702.37, “Morph.”

\subsubsection*{Meld}
\addcontentsline{toc}{subsubsection}{Meld}

To turn two members of a meld pair so their back faces are up and combined into one oversized Magic card. See rule 701.42, “Meld.”

\subsubsection*{Meld Cards}
\addcontentsline{toc}{subsubsection}{Meld Cards}

Cards with a Magic card face on one side and half of an oversized Magic card face on the other. See rule 712, “Double-Faced Cards.”

\subsubsection*{Melee}
\addcontentsline{toc}{subsubsection}{Melee}

A keyword ability that improves an attacking creature based on the number of opponents you attacked. See rule 702.121, “Melee.”

\subsubsection*{Menace}
\addcontentsline{toc}{subsubsection}{Menace}

An evasion ability that makes creatures unblockable by a single creature. See rule 702.111, “Menace.”

\subsubsection*{Mentor}
\addcontentsline{toc}{subsubsection}{Mentor}

A keyword ability that lets your bigger creatures power up your smaller creatures when they attack together. See rule 702.134, “Mentor.”

\subsubsection*{Merged Permanent}
\addcontentsline{toc}{subsubsection}{Merged Permanent}

A card or token may merge with a permanent to form a merged permanent. This merged permanent is represented by more than one card and/or token. See rule 729, “Merging with Permanents.”

\subsubsection*{Mill}
\addcontentsline{toc}{subsubsection}{Mill}

To mill a number of cards, a player puts that many cards from the top of their library into their graveyard. See rule 701.17.

\subsubsection*{Minimum Deck Size}
\addcontentsline{toc}{subsubsection}{Minimum Deck Size}

If a rule or effect states that a player’s deck must contain at least a specific number of cards, that number is the player’s minimum deck size.

\subsubsection*{Miracle}
\addcontentsline{toc}{subsubsection}{Miracle}

A keyword ability that lets you cast a spell for a reduced cost if it’s the first card you draw in a turn. See rule 702.94, “Miracle.”

\subsubsection*{Mobilize}
\addcontentsline{toc}{subsubsection}{Mobilize}

A keyword ability that creates a number of tapped and attacking red Warrior creature tokens that are sacrificed at the beginning of the next end step. See rule 702.181, “Mobilize.”

\subsubsection*{Modal, Mode}
\addcontentsline{toc}{subsubsection}{Modal, Mode}

A spell or ability is “modal” if it has two or more options in a bulleted list preceded by instructions for a player to choose a number of those options, such as “Choose one —.” See rule 700.2.

\subsubsection*{Modal Double-Faced Cards}
\addcontentsline{toc}{subsubsection}{Modal Double-Faced Cards}

One kind of double-faced card. Modal double-faced cards can be played with either of their two faces up. See rule 712, “Double-Faced Cards.”

\subsubsection*{Modified}
\addcontentsline{toc}{subsubsection}{Modified}

A modified creature is a creature that has a counter on it, is equipped, or is enchanted by an Aura its controller also controls. See rule 700.9.

\subsubsection*{Modular}
\addcontentsline{toc}{subsubsection}{Modular}

A keyword ability that has a permanent enter the battlefield with +1/+1 counters on it and can move those counters to other artifact creatures. See rule 702.43, “Modular.”

\subsubsection*{Monarch}
\addcontentsline{toc}{subsubsection}{Monarch}

A designation a player can have. Some effects instruct a player to become the monarch. The monarch draws a card at the beginning of their end step. Dealing combat damage to the monarch steals the title from that player. See rule 724, “The Monarch.”

\subsubsection*{Mono Artifact (Obsolete)}
\addcontentsline{toc}{subsubsection}{Mono Artifact (Obsolete)}

An obsolete term that appeared on the type line of artifacts with activated abilities that caused the artifact to become tapped as a cost. Cards printed with this text have received errata in the Oracle card reference to simply say “Artifact,” and those abilities now include the tap symbol in their costs.

\subsubsection*{Monocolored}
\addcontentsline{toc}{subsubsection}{Monocolored}

An object with exactly one color is monocolored. Colorless objects aren’t monocolored. See rule 105, “Colors,” and rule 202, “Mana Cost and Color.”

\subsubsection*{Monocolored Hybrid Mana Symbols}
\addcontentsline{toc}{subsubsection}{Monocolored Hybrid Mana Symbols}

See Hybrid Mana Symbols.

\subsubsection*{Monstrosity}
\addcontentsline{toc}{subsubsection}{Monstrosity}

A keyword action that puts +1/+1 counters on a creature and makes it become monstrous. See rule 701.37, “Monstrosity.”

\subsubsection*{Monstrous}
\addcontentsline{toc}{subsubsection}{Monstrous}

A designation given to a creature whose ability including a monstrosity instruction has resolved. See rule 701.37, “Monstrosity.”

More Than Meets the Eye

A keyword ability that allows some cards to be cast converted. See rule 702.162, “More Than Meets the Eye,” and rule 701.28, “Convert.”

\subsubsection*{Morph}
\addcontentsline{toc}{subsubsection}{Morph}

A keyword ability that lets a card be cast face down as a 2/2 creature. See rule 702.37, “Morph,” and rule 708, “Face-Down Spells and Permanents.”

\subsubsection*{Mountain}
\addcontentsline{toc}{subsubsection}{Mountain}

One of the five basic land types. Any land with this subtype has the ability “{T: Add {R.” See rule 305.6.

\subsubsection*{Mountaincycling}
\addcontentsline{toc}{subsubsection}{Mountaincycling}

See Typecycling.

\subsubsection*{Mountainwalk}
\addcontentsline{toc}{subsubsection}{Mountainwalk}

See Landwalk.

\subsubsection*{Move}
\addcontentsline{toc}{subsubsection}{Move}

To remove a counter from one object and put it on a different object. See rule 122.5.

Some older cards used “move” with respect to Auras; those cards have received errata in the Oracle card reference and now use the word “attach.”

\subsubsection*{Mulligan}
\addcontentsline{toc}{subsubsection}{Mulligan}

To take a mulligan is to reject a prospective opening hand in favor of a new one. See rule 103.5.

\subsubsection*{Multicolored}
\addcontentsline{toc}{subsubsection}{Multicolored}

An object with two or more colors is multicolored. Multicolored is not a color. See rule 105, “Colors,” and rule 202, “Mana Cost and Color.”

\subsubsection*{Multikicker}
\addcontentsline{toc}{subsubsection}{Multikicker}

Multikicker is a variant of the kicker keyword ability. It represents an optional additional cost that may be paid any number of times. See rule 702.33, “Kicker.” See also Kicker.

\subsubsection*{Multiplayer Game}
\addcontentsline{toc}{subsubsection}{Multiplayer Game}

A game that begins with more than two players. See section 8, “Multiplayer Rules.”

\subsubsection*{Mutate}
\addcontentsline{toc}{subsubsection}{Mutate}

A keyword that lets a creature card be cast as a mutating creature spell. See rule 702.140, “Mutate.”

\subsubsection*{Mutating Creature Spell}
\addcontentsline{toc}{subsubsection}{Mutating Creature Spell}

A creature spell cast using the mutate keyword ability. As it resolves, if its target creature is legal, it merges with the target creature. The resulting creature has all characteristics of the topmost component and has the abilities of each component. See rule 702.140, “Mutate,” and rule 729, “Merging with Permanents.”

\subsubsection*{Myriad}
\addcontentsline{toc}{subsubsection}{Myriad}

Myriad is a triggered ability that effectively lets a creature attack in all possible directions. See rule 702.116, “Myriad.”

\subsubsection*{Name}
\addcontentsline{toc}{subsubsection}{Name}

A characteristic, and part of a card. A card’s name is printed in its upper left corner. See rule 201, “Name.”

\subsubsection*{Night}
\addcontentsline{toc}{subsubsection}{Night}

Along with day, a designation the game can have. See rule 730, “Day and Night,” and rule 702.145, “Daybound and Nightbound.”

\subsubsection*{Nightbound}
\addcontentsline{toc}{subsubsection}{Nightbound}

An ability found on the back faces of some double-faced cards. Cards with daybound and nightbound are face up when it’s day and face down when it’s night. See rule 702.145, “Daybound and Nightbound,” and rule 730, “Day and Night.”

\subsubsection*{Ninjutsu}
\addcontentsline{toc}{subsubsection}{Ninjutsu}

A keyword ability that lets a creature suddenly enter combat. See rule 702.49, “Ninjutsu.”

\subsubsection*{Nonbasic Land}
\addcontentsline{toc}{subsubsection}{Nonbasic Land}

Any land that doesn’t have the supertype “basic.” See rule 205.4, “Supertypes.”

\subsubsection*{Nonmodal Double-Faced Card}
\addcontentsline{toc}{subsubsection}{Nonmodal Double-Faced Card}

One kind of double-faced card. Nonmodal double-faced cards default to being cast with their front faces up but can transform to their back faces in some way. See rule 712, “Double-Faced Cards.”

\subsubsection*{Nontraditional Magic Card}
\addcontentsline{toc}{subsubsection}{Nontraditional Magic Card}

A card not included in players’ decks. It may be oversized or have a card back other than a “Deckmaster” back. See rule 108.2.

\subsubsection*{Object}
\addcontentsline{toc}{subsubsection}{Object}

An ability on the stack, a card, a copy of a card, an emblem, a token, a spell, or a permanent. See rule 109, “Objects.”

\subsubsection*{Offering}
\addcontentsline{toc}{subsubsection}{Offering}

A keyword ability that modifies when you can cast a spell and how much mana you need to spend to do it. See rule 702.48, “Offering.”

\subsubsection*{Offspring}
\addcontentsline{toc}{subsubsection}{Offspring}

A keyword ability that allows you to pay an additional cost as you cast a creature spell to create a 1/1 token that’s a copy of that permanent when it enters the battlefield. See rule 702.175, “Offspring.”

\subsubsection*{Omen Card}
\addcontentsline{toc}{subsubsection}{Omen Card}

Cards with a two-part card frame (one part of which is inset on the left) on a single card where the alternative characteristics include the Omen spell type. See rule 720, “Omen Cards.”

\subsubsection*{One-Shot Effect}
\addcontentsline{toc}{subsubsection}{One-Shot Effect}

An effect that does something just once and doesn’t have a duration. See rule 610, “One-Shot Effects.” See also Continuous Effects.

\subsubsection*{Ongoing}
\addcontentsline{toc}{subsubsection}{Ongoing}

A supertype that appears only on scheme cards. See rule 205.4, “Supertypes.”

\subsubsection*{Opening Hand}
\addcontentsline{toc}{subsubsection}{Opening Hand}

The hand of cards a player starts the game with, once the player has decided not to take any further mulligans. See rule 103.5.

\subsubsection*{Opponent}
\addcontentsline{toc}{subsubsection}{Opponent}

Someone a player is playing against. See rules 102.2 and 102.3.

\subsubsection*{Option}
\addcontentsline{toc}{subsubsection}{Option}

An additional rule or set of rules that can be used in a multiplayer game. See rule 800.2.

\subsubsection*{Oracle}
\addcontentsline{toc}{subsubsection}{Oracle}

The reference that contains the up-to-date wordings (in English) for all tournament-legal cards. A card’s Oracle text can be found using the Gatherer card database at Gatherer.Wizards.com. See rule 108.1.

\subsubsection*{Outlast}
\addcontentsline{toc}{subsubsection}{Outlast}

A keyword ability that allows a creature to grow larger over time. See rule 702.107, “Outlast.”

\subsubsection*{Outside the Game}
\addcontentsline{toc}{subsubsection}{Outside the Game}

An object is “outside the game” if it isn’t in any of the game’s zones. See rule 400.11.

\subsubsection*{Overload}
\addcontentsline{toc}{subsubsection}{Overload}

A keyword ability that allows a spell to affect either a single target or many objects. See rule 702.96, “Overload.”

\subsubsection*{Owner}
\addcontentsline{toc}{subsubsection}{Owner}

The player who (for purposes of the game) a card, permanent, token, or spell belongs to. See rules 108.3, 110.2, 111.2, and 112.2.

\subsubsection*{Paired}
\addcontentsline{toc}{subsubsection}{Paired}

A term that describes a creature that’s been affected by a soulbond ability. See rule 702.95, “Soulbond.”

\subsubsection*{Paris Mulligan}
\addcontentsline{toc}{subsubsection}{Paris Mulligan}

Informal term for a previous system of taking a mulligan. Using the Paris mulligan, a player who took a mulligan shuffled their hand into their library and drew one fewer card. For current mulligan rules, see rule 103.5.

Partner, “Partner—[text],” “Partner with [name]”

A keyword ability that lets two legendary cards be your commander in the Commander variant rather than one. “Partner with [name]” is a specialized version of the ability that works even outside of the Commander variant to help two cards reach the battlefield together. See rule 702.124, “Partner,” and rule 903, “Commander.”

\subsubsection*{Party}
\addcontentsline{toc}{subsubsection}{Party}

Some cards refer to the number of creatures in your party. A player’s party includes up to one each of Cleric, Rogue, Warrior, and Wizard. See rule 700.8.

\subsubsection*{Pass}
\addcontentsline{toc}{subsubsection}{Pass}

To decline to take any action (such as casting a spell or activating an ability) when you have priority. See rule 117, “Timing and Priority.”

\subsubsection*{Pass in Succession}
\addcontentsline{toc}{subsubsection}{Pass in Succession}

All players “pass in succession” if each player in the game (starting with any one of them) opts not to take an action upon receiving priority. See rule 117, “Timing and Priority.”

\subsubsection*{Pawprint Symbol}
\addcontentsline{toc}{subsubsection}{Pawprint Symbol}

A symbol shaped like a pawprint that is used to indicate the modes on some modal spells. See rule 700.2i.

\subsubsection*{Pay}
\addcontentsline{toc}{subsubsection}{Pay}

To perform the actions required by a cost. This often means, but is not restricted to, spending resources such as mana or life. See rule 118, “Costs.”

\subsubsection*{Permanent}
\addcontentsline{toc}{subsubsection}{Permanent}

A card or token on the battlefield. See rule 110, “Permanents.”

\subsubsection*{Permanent Card}
\addcontentsline{toc}{subsubsection}{Permanent Card}

A card that could be put onto the battlefield. See rule 110.4a.

\subsubsection*{Permanent Spell}
\addcontentsline{toc}{subsubsection}{Permanent Spell}

A spell that will enter the battlefield as a permanent as part of its resolution. See rule 110.4b.

\subsubsection*{Permanently (Obsolete)}
\addcontentsline{toc}{subsubsection}{Permanently (Obsolete)}

An obsolete term used to indicate that a continuous effect has no duration and thus lasts until the end of the game. Cards printed with this term have received errata in the Oracle card reference to delete it.

\subsubsection*{Persist}
\addcontentsline{toc}{subsubsection}{Persist}

A keyword ability that can return a creature from the graveyard to the battlefield. See rule 702.79, “Persist.”

\subsubsection*{Phase}
\addcontentsline{toc}{subsubsection}{Phase}

A subsection of a turn. See section 5, “Turn Structure.”
A permanent “phases in” when its status changes from phased out to phased in. A permanent “phases out” when its status changes from phased in to phased out. See rule 702.26, “Phasing.”

\subsubsection*{Phased In, Phased Out}
\addcontentsline{toc}{subsubsection}{Phased In, Phased Out}

A status a permanent may have. Phased-in is the default status. Phased-out permanents are treated as though they do not exist. See rule 110.5 and rule 702.26, “Phasing.” (“Phased-out” was a zone in older versions of the rules.)

\subsubsection*{Phasing}
\addcontentsline{toc}{subsubsection}{Phasing}

A keyword ability that causes a permanent to sometimes be treated as though it does not exist. See rule 702.26, “Phasing.”

\subsubsection*{Phenomenon}
\addcontentsline{toc}{subsubsection}{Phenomenon}

A card type seen only on nontraditional Magic cards in the Planechase casual variant. A phenomenon card is not a permanent. See rule 312, “Phenomena.”

\subsubsection*{Phyrexian Mana Symbol}
\addcontentsline{toc}{subsubsection}{Phyrexian Mana Symbol}

A mana symbol that represents a cost that can be paid either by spending colored mana or by paying life. See rule 107.4.

\subsubsection*{Phyrexian Symbol}
\addcontentsline{toc}{subsubsection}{Phyrexian Symbol}

A symbol used in rules text to represent any of the five Phyrexian mana symbols. See rule 107.4g.

\subsubsection*{Pile}
\addcontentsline{toc}{subsubsection}{Pile}

A temporary grouping of cards. See rule 700.3.

\subsubsection*{Placed}
\addcontentsline{toc}{subsubsection}{Placed}

(Obsolete) Some spells and abilities previously referred to a counter being “placed” on a permanent. These cards have received errata in the Oracle card reference to use the term “put” instead. Due to a rules change, these cards continue to function as they did before. See rule 122, “Counters.”

\subsubsection*{Plains}
\addcontentsline{toc}{subsubsection}{Plains}

One of the five basic land types. Any land with this subtype has the ability “{T: Add {W.” See rule 305.6.

\subsubsection*{Plainscycling}
\addcontentsline{toc}{subsubsection}{Plainscycling}

See Typecycling.

\subsubsection*{Plainswalk}
\addcontentsline{toc}{subsubsection}{Plainswalk}

See Landwalk.

\subsubsection*{Planar Deck}
\addcontentsline{toc}{subsubsection}{Planar Deck}

A deck of at least ten plane cards needed to play the Planechase casual variant. See rule 901.3.

\subsubsection*{Planar Die}
\addcontentsline{toc}{subsubsection}{Planar Die}

A specialized six-sided die needed to play the Planechase casual variant. See rule 901.3.

\subsubsection*{Plane}
\addcontentsline{toc}{subsubsection}{Plane}

A card type seen only on nontraditional Magic cards in the Planechase casual variant. A plane card is not a permanent. See rule 311, “Planes.”

\subsubsection*{Planechase}
\addcontentsline{toc}{subsubsection}{Planechase}

A casual variant in which plane cards and phenomenon cards add additional abilities and randomness to the game. See rule 901, “Planechase.”

\subsubsection*{Planeswalk}
\addcontentsline{toc}{subsubsection}{Planeswalk}

To put each face-up plane card or phenomenon card on the bottom of its owner’s planar deck face down, then move the top card of your planar deck off that planar deck and turn it face up in a Planechase game. See rule 701.31, “Planeswalk.”

\subsubsection*{Planeswalker}
\addcontentsline{toc}{subsubsection}{Planeswalker}

A card type. A planeswalker is a permanent. See rule 306, “Planeswalkers.”

\subsubsection*{Planeswalker Symbol}
\addcontentsline{toc}{subsubsection}{Planeswalker Symbol}

The Planeswalker symbol appears on the planar die in the Planechase casual variant. See rule 107.11.

\subsubsection*{Planeswalker Type}
\addcontentsline{toc}{subsubsection}{Planeswalker Type}

A subtype that’s correlated to the planeswalker card type. See rule 306, “Planeswalkers.” See rule 205.3j for the list of planeswalker types.

\subsubsection*{Planeswalker Uniqueness Rule (Obsolete)}
\addcontentsline{toc}{subsubsection}{Planeswalker Uniqueness Rule (Obsolete)}

Older versions of the rules stated that a player who controlled two or more planeswalkers with the same planeswalker type would put all but one of those planeswalkers into their owners’ graveyards. This rule was called the “planeswalker uniqueness rule” and no longer exists.

\subsubsection*{Play}
\addcontentsline{toc}{subsubsection}{Play}

To play a land is to put a land onto the battlefield as a special action. See rule 116, “Special Actions,” and rule 305, “Lands.” To play a card is to play that card as a land or cast that card as a spell, whichever is appropriate. See rule 601, “Casting Spells.”

3. (Obsolete) Casting a spell used to be known as playing a spell. Cards with that text have received errata in the Oracle card reference. See Cast.

4. (Obsolete) Activating an activated ability used to be known as playing an activated ability. Cards with that text have received errata in the Oracle card reference. See Activate.

5. (Obsolete) The battlefield used to be known as the in-play zone. Cards that were printed with text that contains the phrases “in play,” “from play,” “into play,” or the like are referring to the battlefield and have received errata in the Oracle card reference. See Battlefield.

\subsubsection*{Player}
\addcontentsline{toc}{subsubsection}{Player}

One of the people in the game. See rule 102, “Players.”

\subsubsection*{Plot}
\addcontentsline{toc}{subsubsection}{Plot}

A keyword ability that lets a player exile cards from their hand and cast them without paying their mana cost on future turns. See rule 702.170, “Plot.”

\subsubsection*{Plotted}
\addcontentsline{toc}{subsubsection}{Plotted}

A card exiled using the plot special action becomes plotted. Other effects can also make an exiled card plotted. See rule 702.170, “Plot.”

\subsubsection*{Poison Counter}
\addcontentsline{toc}{subsubsection}{Poison Counter}

A counter that may be given to a player. See rule 122, “Counters,” and rule 704.5c.

\subsubsection*{Poisoned}
\addcontentsline{toc}{subsubsection}{Poisoned}

Having one or more poison counters. See rule 122, “Counters.”

\subsubsection*{Poisonous}
\addcontentsline{toc}{subsubsection}{Poisonous}

A keyword ability that causes a player to get poison counters. See rule 702.70, “Poisonous.”

\subsubsection*{Poly Artifact (Obsolete)}
\addcontentsline{toc}{subsubsection}{Poly Artifact (Obsolete)}

An obsolete term that appeared on the type line of artifacts with activated abilities that didn’t cause the artifact to be tapped as a cost. Cards printed with this text have received errata in the Oracle card reference to simply say “Artifact.”

\subsubsection*{Populate}
\addcontentsline{toc}{subsubsection}{Populate}

A keyword action that creates a copy of a creature token you control. See rule 701.36, “Populate.”

\subsubsection*{Postcombat Main Phase}
\addcontentsline{toc}{subsubsection}{Postcombat Main Phase}

A main phase that occurs after a combat phase. See Main Phase.

\subsubsection*{Power}
\addcontentsline{toc}{subsubsection}{Power}

Part of a card that only creature cards have. A creature card’s power is printed before the slash in its lower right corner. See rule 208, “Power/Toughness.”
A characteristic that only creatures have. See rule 302.4.

\subsubsection*{Powerstone Token}
\addcontentsline{toc}{subsubsection}{Powerstone Token}

A Powerstone token is a colorless artifact token with “{T: Add {C. This mana can’t be spent to cast a nonartifact spell.” For more information about predefined tokens, see rule 111.10.

\subsubsection*{Precombat Main Phase}
\addcontentsline{toc}{subsubsection}{Precombat Main Phase}

The first main phase of a turn. See Main Phase.

\subsubsection*{Prevent}
\addcontentsline{toc}{subsubsection}{Prevent}

A word used by prevention effects to indicate what damage will not be dealt. See rule 615, “Prevention Effects.”

\subsubsection*{Prevention Effect}
\addcontentsline{toc}{subsubsection}{Prevention Effect}

A kind of continuous effect that watches for a damage event that would happen and completely or partially prevents the damage that would be dealt. See rule 615, “Prevention Effects.”

\subsubsection*{Priority}
\addcontentsline{toc}{subsubsection}{Priority}

Which player can take actions at any given time is determined by a system of “priority.” See rule 117, “Timing and Priority.”

\subsubsection*{Prize}
\addcontentsline{toc}{subsubsection}{Prize}

An additional reward for visiting some Attractions. See rule 702.159, “Visit.”

\subsubsection*{Proliferate}
\addcontentsline{toc}{subsubsection}{Proliferate}

To give an additional counter to any number of players and/or permanents of each kind they already have. See rule 701.34, “Proliferate.”

\subsubsection*{Protect, Protector}
\addcontentsline{toc}{subsubsection}{Protect, Protector}

Each battle has a player designated as its protector, and that player protects that battle. See rule 310.8.

\subsubsection*{Protection}
\addcontentsline{toc}{subsubsection}{Protection}

A keyword ability that provides a range of benefits against objects with a specific quality. See rule 702.16, “Protection.”

\subsubsection*{Prototype}
\addcontentsline{toc}{subsubsection}{Prototype}

An ability which allows a prototype card to be cast with a secondary set of characteristics. See rule 718, “Prototype Cards,” and rule 702.160, “Prototype.”

\subsubsection*{Prototype Card}
\addcontentsline{toc}{subsubsection}{Prototype Card}

Cards with a two-part card frame (one part of which is inset under the type line) on a single card. See rule 718, “Prototype Cards.”

\subsubsection*{Provoke}
\addcontentsline{toc}{subsubsection}{Provoke}

A keyword ability that can force a creature to block. See rule 702.39, “Provoke.”

\subsubsection*{Prowess}
\addcontentsline{toc}{subsubsection}{Prowess}

A keyword ability that causes a creature to get +1/+1 whenever its controller casts a noncreature spell. See rule 702.108, “Prowess.”

\subsubsection*{Prowl}
\addcontentsline{toc}{subsubsection}{Prowl}

A keyword ability that may allow a spell to be cast for an alternative cost. See rule 702.76, “Prowl.”

\subsubsection*{Public Zone}
\addcontentsline{toc}{subsubsection}{Public Zone}

A zone in which all players can be expected to see the cards’ faces. See rule 400.2. See also Hidden Zone.

\subsubsection*{Rad Counter}
\addcontentsline{toc}{subsubsection}{Rad Counter}

A type of counter a player can have that causes that player to mill cards at the beginning of their precombat main phase, then lose 1 life and remove one rad counter for each nonland card milled this way. See rule 122, “Counters,” and rule 727, “Rad Counters.”

\subsubsection*{Rampage}
\addcontentsline{toc}{subsubsection}{Rampage}

A keyword ability that can make a creature better in combat. See rule 702.23, “Rampage.”

\subsubsection*{Range of Influence}
\addcontentsline{toc}{subsubsection}{Range of Influence}

See Limited Range of Influence.

\subsubsection*{Ravenous}
\addcontentsline{toc}{subsubsection}{Ravenous}

A keyword ability found on some creature cards with {X in their mana cost. The creature enters the battlefield with X +1/+1 counters on it, and you draw a card if X is 5 or more. See rule 702.156, “Ravenous.”

\subsubsection*{Reach}
\addcontentsline{toc}{subsubsection}{Reach}

A keyword ability that allows a creature to block an attacking creature with flying. See rule 702.17, “Reach.” See also Flying.

\subsubsection*{Read Ahead}
\addcontentsline{toc}{subsubsection}{Read Ahead}

A keyword ability found on some Sagas that allows their controller to choose which chapter it starts on. See rule 702.155, “Read Ahead.”

\subsubsection*{Rebound}
\addcontentsline{toc}{subsubsection}{Rebound}

A keyword ability that allows an instant or sorcery spell to be cast a second time. See rule 702.88, “Rebound.”

\subsubsection*{Reconfigure}
\addcontentsline{toc}{subsubsection}{Reconfigure}

A keyword ability that allows an Equipment creature to temporarily stop being a creature and become attached to another creature. See rule 702.151, “Reconfigure.”

\subsubsection*{Recover}
\addcontentsline{toc}{subsubsection}{Recover}

A keyword ability that lets a player return a card from their graveyard to their hand. See rule 702.59, “Recover.”

\subsubsection*{Redirect (Obsolete)}
\addcontentsline{toc}{subsubsection}{Redirect (Obsolete)}

Some older cards were printed with the term “redirect” to indicate a redirection effect. Such cards have received errata in the Oracle card reference so they explicitly state that damage that would be dealt to one object or player is dealt “instead” to another. See Redirection Effect.

\subsubsection*{Redirection Effect}
\addcontentsline{toc}{subsubsection}{Redirection Effect}

A kind of replacement effect that causes damage that would be dealt to one creature, planeswalker, or player to be dealt instead to another creature, planeswalker, or player. See rule 614.9.

\subsubsection*{Reflexive Triggered Ability}
\addcontentsline{toc}{subsubsection}{Reflexive Triggered Ability}

An ability that triggers based on actions taken earlier during a spell or ability’s resolution. See rule 603.12.

\subsubsection*{Regenerate}
\addcontentsline{toc}{subsubsection}{Regenerate}

To replace a permanent’s destruction with an alternate sequence of events. See rule 701.19, “Regenerate.”

\subsubsection*{Reinforce}
\addcontentsline{toc}{subsubsection}{Reinforce}

A keyword ability that lets a player put +1/+1 counters on a creature. See rule 702.77, “Reinforce.”

\subsubsection*{Reminder Text}
\addcontentsline{toc}{subsubsection}{Reminder Text}

Parenthetical text in italics in the text box of a card that summarizes a rule that applies to that card, but is not actually rules text and has no effect on play. See rule 207.2.

\subsubsection*{Removed from Combat}
\addcontentsline{toc}{subsubsection}{Removed from Combat}

Certain events can cause an attacking or blocking creature, or a planeswalker that’s being attacked, to be “removed from combat.” A permanent that’s removed from combat has no further involvement in that combat phase. See rule 506.4.

Remove from the Game, Removed, Removed-from-the-Game Zone (Obsolete)

“Remove [something] from the game” is an obsolete term for “exile [something].” “The removed card” is an obsolete term for “the exiled card.” The removed-from-the-game zone is an obsolete term for the exile zone. Cards with that text have received errata in the Oracle card reference. See Exile.

\subsubsection*{Renown}
\addcontentsline{toc}{subsubsection}{Renown}

A keyword ability that makes a creature stronger after it deals combat damage to a player. See rule 702.112, “Renown.”

\subsubsection*{Renowned}
\addcontentsline{toc}{subsubsection}{Renowned}

A designation given to a permanent as a result of the renown ability. See rule 702.112, “Renown.”

\subsubsection*{Replacement Effect}
\addcontentsline{toc}{subsubsection}{Replacement Effect}

A kind of continuous effect that watches for a particular event that would happen and completely or partially replaces that event with a different event. See rule 614, “Replacement Effects.”

\subsubsection*{Replicate}
\addcontentsline{toc}{subsubsection}{Replicate}

A keyword ability that creates copies of a spell. See rule 702.56, “Replicate.”

\subsubsection*{Requirement}
\addcontentsline{toc}{subsubsection}{Requirement}

An effect that forces one or more creatures to attack or block. See rules 508.1d and 509.1c.

\subsubsection*{Resolve}
\addcontentsline{toc}{subsubsection}{Resolve}

When the spell or ability on top of the stack “resolves,” its instructions are followed and it has its effect. See rule 608, “Resolving Spells and Abilities.”

\subsubsection*{Restart the Game}
\addcontentsline{toc}{subsubsection}{Restart the Game}

To immediately end the current game and restart it. See rule 104, “Ending the Game.”

\subsubsection*{Respond}
\addcontentsline{toc}{subsubsection}{Respond}

To cast an instant spell or activate an ability while another spell or ability is already on the stack. See rule 117.7.

\subsubsection*{Restriction}
\addcontentsline{toc}{subsubsection}{Restriction}

An effect that precludes one or more creatures from attacking or blocking. See rules 508.1c and 509.1b.

\subsubsection*{Retrace}
\addcontentsline{toc}{subsubsection}{Retrace}

A keyword ability that lets a player cast a card from their graveyard. See rule 702.81, “Retrace.”

\subsubsection*{Reveal}
\addcontentsline{toc}{subsubsection}{Reveal}

To show a card to all players for a brief time. See rule 701.20, “Reveal.”

\subsubsection*{The Ring}
\addcontentsline{toc}{subsubsection}{The Ring}

An emblem that may be created at the time the Ring tempts you. See rule 701.54, “The Ring Tempts You.”

\subsubsection*{The Ring Tempts You}
\addcontentsline{toc}{subsubsection}{The Ring Tempts You}

A keyword action that causes a player to choose a creature they control to be their legendary Ring-bearer and may cause them to create an emblem called The Ring. See rule 701.54, “The Ring Tempts You.”

\subsubsection*{Ring-bearer}
\addcontentsline{toc}{subsubsection}{Ring-bearer}

A designation that a creature can be given as the Ring tempts you. See rule 701.54, “The Ring Tempts You.”

\subsubsection*{Riot}
\addcontentsline{toc}{subsubsection}{Riot}

A keyword ability that lets a player choose whether certain creatures enter the battlefield with haste or with a +1/+1 counter. See rule 702.136, “Riot.”

\subsubsection*{Ripple}
\addcontentsline{toc}{subsubsection}{Ripple}

A keyword ability that may let a player cast extra cards from their library for no cost. See rule 702.60, “Ripple.”

\subsubsection*{Role}
\addcontentsline{toc}{subsubsection}{Role}

Roles are colorless enchantment tokens. Each one has the Aura and Role subtypes and the enchant creature ability. If a permanent has more than one Role attached to it controlled by the same player, each of those Roles except the one with the most recent timestamp is put into its owner’s graveyard. See rule 303.7 and rules 111.10j–r.

\subsubsection*{Roll a d20}
\addcontentsline{toc}{subsubsection}{Roll a d20}

To roll a twenty-sided die. Similarly, a d4 is a four-sided die, a d6 is a six-sided die, and so on. See rule 706, “Rolling a Die.”

\subsubsection*{Room}
\addcontentsline{toc}{subsubsection}{Room}

A subsection of a dungeon card. See rule 309, “Dungeons.”
An enchantment subtype found on some split cards. See rule 709, “Split Cards.”

\subsubsection*{Room Ability}
\addcontentsline{toc}{subsubsection}{Room Ability}

A triggered ability that triggers whenever a player moves their venture marker into a room of a dungeon card. See rule 309, “Dungeons.”

\subsubsection*{Rules Text}
\addcontentsline{toc}{subsubsection}{Rules Text}

A characteristic that defines a card’s abilities. See rule 207.1.

\subsubsection*{Sacrifice}
\addcontentsline{toc}{subsubsection}{Sacrifice}

To move a permanent you control to its owner’s graveyard. See rule 701.21, “Sacrifice.”

\subsubsection*{Saddle}
\addcontentsline{toc}{subsubsection}{Saddle}

A keyword ability that lets you tap creatures to make another creature “saddled” until end of turn. See rule 702.171, “Saddle.”

\subsubsection*{Saddled}
\addcontentsline{toc}{subsubsection}{Saddled}

A designation given to a creature whose saddle ability has resolved. See rule 702.171, “Saddle.”

\subsubsection*{Saga}
\addcontentsline{toc}{subsubsection}{Saga}

An enchantment subtype. Sagas have a number of chapter abilities that take effect over a number of turns to tell a story. See rule 714, “Saga Cards.”

\subsubsection*{Scavenge}
\addcontentsline{toc}{subsubsection}{Scavenge}

A keyword ability that allows you to exile a creature card from your graveyard to put +1/+1 counters on a creature. See rule 702.97, “Scavenge.”

\subsubsection*{Scheme}
\addcontentsline{toc}{subsubsection}{Scheme}

A card type seen only on nontraditional Magic cards in the Archenemy casual variant. A scheme card is not a permanent. See rule 314, “Schemes.”

\subsubsection*{Scheme Deck}
\addcontentsline{toc}{subsubsection}{Scheme Deck}

A deck of at least twenty scheme cards needed to play the Archenemy casual variant. See rule 904.3.

\subsubsection*{Scry}
\addcontentsline{toc}{subsubsection}{Scry}

To manipulate some of the cards on top of your library. See rule 701.22, “Scry.”

\subsubsection*{Search}
\addcontentsline{toc}{subsubsection}{Search}

To look at all cards in a stated zone and possibly find a card that matches a given description. See rule 701.23, “Search.”

\subsubsection*{Secondary Title Bar}
\addcontentsline{toc}{subsubsection}{Secondary Title Bar}

A smaller name line with the Oracle reference name of a card which has an alternate name in its upper left corner. See rule 201.6.

\subsubsection*{Set Aside (Obsolete)}
\addcontentsline{toc}{subsubsection}{Set Aside (Obsolete)}

“Set [something] aside” is an obsolete term for “exile [something].” Cards with that text have received errata in the Oracle card reference. See Exile.

\subsubsection*{Set in Motion}
\addcontentsline{toc}{subsubsection}{Set in Motion}

To move a scheme card off the top of your scheme deck and turn it face up. See rule 701.32, “Set in Motion.”

\subsubsection*{Shadow}
\addcontentsline{toc}{subsubsection}{Shadow}

A keyword ability that restricts how a creature may be blocked and which creatures it can block. See rule 702.28, “Shadow.”

\subsubsection*{Shard Token}
\addcontentsline{toc}{subsubsection}{Shard Token}

A Shard token is a colorless enchantment token with “{2, Sacrifice this token: Scry 1, then draw a card.” For more information on predefined tokens, see rule 111.10.

\subsubsection*{Shared Life Total}
\addcontentsline{toc}{subsubsection}{Shared Life Total}

In the Two-Headed Giant multiplayer variant, each team has a “shared life total” rather than each player having an individual life total. See rule 810, “Two-Headed Giant Variant.”

\subsubsection*{Shared Team Turns Option}
\addcontentsline{toc}{subsubsection}{Shared Team Turns Option}

An option that may be used in certain multiplayer variants, such as Two-Headed Giant and Archenemy. See rule 805, “Shared Team Turns Option.”

\subsubsection*{Shield Counter}
\addcontentsline{toc}{subsubsection}{Shield Counter}

A counter that protects a permanent from being damaged or destroyed. See rule 122.1c.

\subsubsection*{Shortcut}
\addcontentsline{toc}{subsubsection}{Shortcut}

A mutually understood way for the game to advance forward a number of game choices (either taking an action or passing priority) without players needing to explicitly identify each such choice. See rule 731, “Taking Shortcuts.”

\subsubsection*{Shroud}
\addcontentsline{toc}{subsubsection}{Shroud}

A keyword ability that precludes a permanent or player from being targeted. See rule 702.18, “Shroud.”

\subsubsection*{Shuffle}
\addcontentsline{toc}{subsubsection}{Shuffle}

To randomize the cards in a deck (before a game) or library (during a game). See rule 103.3 and rule 701.24.

\subsubsection*{Sideboard}
\addcontentsline{toc}{subsubsection}{Sideboard}

Extra cards that may be used to modify a deck between games of a match. See rules 100.4.

\subsubsection*{Siege}
\addcontentsline{toc}{subsubsection}{Siege}

A battle subtype. Only an opponent of a Siege’s controller can be its protector. When the last defense counter is removed, its controller exiles the Siege, then they may cast it transformed without paying its mana cost. See rule 310.11.

\subsubsection*{Silver-Bordered}
\addcontentsline{toc}{subsubsection}{Silver-Bordered}

Cards in certain sets and certain promotional cards are printed with a silver border. Silver-bordered cards are intended for casual play and may have features and text that aren’t covered by these rules.

\subsubsection*{Skip}
\addcontentsline{toc}{subsubsection}{Skip}

Effects that use the word “skip” are replacement effects. The word “skip” indicates what events, steps, phases, or turns will be replaced with nothing. See rule 614, “Replacement Effects.”

\subsubsection*{Skulk}
\addcontentsline{toc}{subsubsection}{Skulk}

A keyword ability that restricts how a creature may be blocked. See rule 702.118, “Skulk.”

\subsubsection*{Slivercycling}
\addcontentsline{toc}{subsubsection}{Slivercycling}

See Typecycling.

\subsubsection*{Sneak}
\addcontentsline{toc}{subsubsection}{Sneak}

A keyword ability that allows a spell to be cast for an alternative cost, including returning an unblocked attacking creature to its owner’s hand. Creatures cast this way enter tapped and attacking.

\subsubsection*{Snow}
\addcontentsline{toc}{subsubsection}{Snow}

A supertype that’s normally relevant on permanents. See rule 205.4, “Supertypes.”

\subsubsection*{Snow Mana Symbol}
\addcontentsline{toc}{subsubsection}{Snow Mana Symbol}

The snow mana symbol {S represents a cost that can be paid with one mana produced by a snow source. It can also represent mana from a snow source that was spent to pay a cost. See rule 107.4h.

\subsubsection*{Snow-Covered (Obsolete)}
\addcontentsline{toc}{subsubsection}{Snow-Covered (Obsolete)}

Some older cards were printed with the term “snow-covered” in their rules text. Except when referencing card names, such cards have received errata in the Oracle card reference to reference the supertype “snow” instead. See Snow.

\subsubsection*{Solved}
\addcontentsline{toc}{subsubsection}{Solved}

A designation a Case may have, allowing its last ability to affect the game. See rule 719, “Case Cards.”
A keyword ability of Case cards that affects the game only if the Case has the solved designation. See rule 702.169, “Solved.”

\subsubsection*{Sorcery}
\addcontentsline{toc}{subsubsection}{Sorcery}

A card type. A sorcery is not a permanent. See rule 307, “Sorceries.”

\subsubsection*{Soulbond}
\addcontentsline{toc}{subsubsection}{Soulbond}

A keyword ability that makes creatures better by pairing them together. See rule 702.95, “Soulbond.”

\subsubsection*{Soulshift}
\addcontentsline{toc}{subsubsection}{Soulshift}

A keyword ability that lets a player return a card from their graveyard to their hand. See rule 702.46, “Soulshift.”

\subsubsection*{Source of an Ability}
\addcontentsline{toc}{subsubsection}{Source of an Ability}

The object that generated that ability. See rule 113.7.

\subsubsection*{Source of Damage}
\addcontentsline{toc}{subsubsection}{Source of Damage}

The object that dealt that damage. See rule 609.7.

\subsubsection*{Source of Mana}
\addcontentsline{toc}{subsubsection}{Source of Mana}

The spell that produced mana or the source of the ability that produced mana. See rule 106.3.

\subsubsection*{Space Sculptor}
\addcontentsline{toc}{subsubsection}{Space Sculptor}

A keyword ability that splits creatures on the battlefield into sectors. See rule 702.158, “Space Sculptor.”

\subsubsection*{Special Action}
\addcontentsline{toc}{subsubsection}{Special Action}

An action a player may take that doesn’t use the stack. See rule 116, “Special Actions.”

\subsubsection*{Spectacle}
\addcontentsline{toc}{subsubsection}{Spectacle}

A keyword ability that allows certain spells to be cast for an alternative cost if an opponent has lost life. See rule 702.137, “Spectacle.”

\subsubsection*{Speed}
\addcontentsline{toc}{subsubsection}{Speed}

Speed is a value that a player can have. See rule 702.179, “Start Your Engines!”

\subsubsection*{Spell}
\addcontentsline{toc}{subsubsection}{Spell}

A card on the stack. Also a copy (of either a card or another spell) on the stack. See rule 112, “Spells.”

\subsubsection*{Spell Ability}
\addcontentsline{toc}{subsubsection}{Spell Ability}

A kind of ability. Spell abilities are abilities that are followed as instructions while an instant or sorcery spell is resolving. See rule 113.3a.

\subsubsection*{Spell Type}
\addcontentsline{toc}{subsubsection}{Spell Type}

A subtype that’s correlated to the instant card type and the sorcery card type. See rule 304, “Instants,” and rule 307, “Sorceries.” See rule 205.3k for the list of spell types.

\subsubsection*{Splice}
\addcontentsline{toc}{subsubsection}{Splice}

A keyword ability that lets a player add a card’s rules text onto another spell. See rule 702.47, “Splice.”

\subsubsection*{Split Cards}
\addcontentsline{toc}{subsubsection}{Split Cards}

Cards with two card faces on a single card. See rule 709, “Split Cards.”

\subsubsection*{Split Second}
\addcontentsline{toc}{subsubsection}{Split Second}

A keyword ability that makes it nearly impossible for a player to respond to a spell. See rule 702.61, “Split Second.”

\subsubsection*{Spree}
\addcontentsline{toc}{subsubsection}{Spree}

An ability found on some modal spells that allows you to choose one or more modes and requires you to pay additional costs for those modes. See rule 702.172, “Spree.”

\subsubsection*{Squad}
\addcontentsline{toc}{subsubsection}{Squad}

A keyword ability that creates copies of a creature when it enters the battlefield. See rule 702.157, “Squad.”

\subsubsection*{Stack}
\addcontentsline{toc}{subsubsection}{Stack}

A zone. The stack is the zone in which spells, activated abilities, and triggered abilities wait to resolve. See rule 405, “Stack.”

\subsubsection*{Start Your Engines!}
\addcontentsline{toc}{subsubsection}{Start Your Engines!}

A keyword ability that gives a player a speed of 1 if they have no speed. Once a player has speed, their speed increases once on each of their turns when an opponent loses life. See rule 702.179, “Start Your Engines!”

\subsubsection*{Starting Deck}
\addcontentsline{toc}{subsubsection}{Starting Deck}

After a player has set aside their sideboard, their remaining deck becomes their starting deck. See rule 103.2a.

\subsubsection*{Starting Hand Size}
\addcontentsline{toc}{subsubsection}{Starting Hand Size}

The number of cards a player draws as a game begins. In most games, each player’s starting hand size is seven. See rule 103.5.

\subsubsection*{Starting Life Total}
\addcontentsline{toc}{subsubsection}{Starting Life Total}

The amount of life a player has as a game begins. In most games, each player’s starting life total is 20. See rule 103.4.

\subsubsection*{Starting Player}
\addcontentsline{toc}{subsubsection}{Starting Player}

The player chosen to take the first turn of a game. See rule 103.1.

\subsubsection*{Starting Team}
\addcontentsline{toc}{subsubsection}{Starting Team}

The team chosen to take the first turn of a game using the shared team turns option. See rule 103.1.

\subsubsection*{State-Based Actions}
\addcontentsline{toc}{subsubsection}{State-Based Actions}

Game actions that happen automatically whenever certain conditions are met. See rule 704, “State-Based Actions.”

\subsubsection*{State Trigger}
\addcontentsline{toc}{subsubsection}{State Trigger}

A triggered ability that triggers when a game state is true rather than triggering when an event occurs. See rule 603.8.

\subsubsection*{Static Ability}
\addcontentsline{toc}{subsubsection}{Static Ability}

A kind of ability. Static abilities do something all the time rather than being activated or triggered. See rule 113, “Abilities,” and rule 604, “Handling Static Abilities.”

\subsubsection*{Station}
\addcontentsline{toc}{subsubsection}{Station}

A keyword ability that lets you tap creatures to add charge counters to station cards. See rule 702.184, “Station,” and rule 721, “Station Cards.”

\subsubsection*{Station Cards}
\addcontentsline{toc}{subsubsection}{Station Cards}

Cards with striated text boxes, one or more station symbols, and the station ability. See rule 721, “Station Cards.”

\subsubsection*{Status}
\addcontentsline{toc}{subsubsection}{Status}

The physical state of a permanent. See rule 110.5.

\subsubsection*{Step}
\addcontentsline{toc}{subsubsection}{Step}

A subsection of a phase. See section 5, “Turn Structure.”

\subsubsection*{Sticker}
\addcontentsline{toc}{subsubsection}{Sticker}

A marker placed on an object that modifies its characteristics or interacts with a rule or effect. See rule 123, “Stickers.”

\subsubsection*{Sticker Kicker}
\addcontentsline{toc}{subsubsection}{Sticker Kicker}

A kicker variant that can add a sticker to the spell with the ability and give a player a ticket counter. See rule 702.33h.

\subsubsection*{Sticker Sheet}
\addcontentsline{toc}{subsubsection}{Sticker Sheet}

The collection of stickers found on an insert in Unfinity booster packs. See rule 123, “Stickers.”

\subsubsection*{Storm}
\addcontentsline{toc}{subsubsection}{Storm}

A keyword ability that creates copies of a spell. See rule 702.40, “Storm.”

\subsubsection*{Stun Counter}
\addcontentsline{toc}{subsubsection}{Stun Counter}

A counter that stops a permanent from untapping. See rule 122.1d.

\subsubsection*{Subgame}
\addcontentsline{toc}{subsubsection}{Subgame}

A completely separate Magic game created by an effect. See rule 728, “Subgames.”

\subsubsection*{Substitute Card}
\addcontentsline{toc}{subsubsection}{Substitute Card}

A game supplement with a Magic card back that can be used to represent a double-faced card or meld card. See rule 713, “Substitute Cards.”

\subsubsection*{Subtype}
\addcontentsline{toc}{subsubsection}{Subtype}

A characteristic that appears after the card type and a long dash on a card’s type line. See rule 205.3, “Subtypes.”

\subsubsection*{Successfully Cast (Obsolete)}
\addcontentsline{toc}{subsubsection}{Successfully Cast (Obsolete)}

A term that was printed on some older cards. In general, cards that referred to a spell being “successfully cast” have received errata in the Oracle card reference to simply refer to a spell being “cast.”

\subsubsection*{Summon (Obsolete)}
\addcontentsline{toc}{subsubsection}{Summon (Obsolete)}

Older creature cards were printed with “Summon [creature type]” on their type lines. All such cards have received errata in the Oracle card reference to say “Creature — [creature type].” (Many of these cards’ creature types have also been updated.) See Creature.

\subsubsection*{Summoning Sickness Rule}
\addcontentsline{toc}{subsubsection}{Summoning Sickness Rule}

Informal term for a player’s inability to attack with a creature or to activate its abilities that include the tap symbol or the untap symbol unless the creature has been under that player’s control since the beginning of that player’s most recent turn. See rule 302.6. See also Haste.

\subsubsection*{Sunburst}
\addcontentsline{toc}{subsubsection}{Sunburst}

A keyword ability that can have a permanent enter the battlefield with +1/+1 counters or charge counters on it. See rule 702.44, “Sunburst.”

\subsubsection*{Supertype}
\addcontentsline{toc}{subsubsection}{Supertype}

A characteristic that appears before the card type on a card’s type line. Most cards don’t have a supertype. See rule 205.4, “Supertypes.”

\subsubsection*{Supervillain Rumble}
\addcontentsline{toc}{subsubsection}{Supervillain Rumble}

A Free-for-All game in which each player is an archenemy. See rule 806, “Free-for-All,” and rule 904, “Archenemy.”

\subsubsection*{Support}
\addcontentsline{toc}{subsubsection}{Support}

A keyword action that lets you put +1/+1 counters on creatures. See rule 701.41, “Support.”

\subsubsection*{Surge}
\addcontentsline{toc}{subsubsection}{Surge}

A keyword ability that provides an alternative cost to cast a card if you or one of your teammates has cast another spell in the same turn. See rule 702.117, “Surge.”

\subsubsection*{Surveil}
\addcontentsline{toc}{subsubsection}{Surveil}

To manipulate some of the cards on top of your library, sending some of them to your graveyard and rearranging the rest. See rule 701.25, “Surveil.”

\subsubsection*{Suspend}
\addcontentsline{toc}{subsubsection}{Suspend}

A keyword ability that provides an alternative way to play a card. See rule 702.62, “Suspend.” A card is “suspended” if it’s in the exile zone, has suspend, and has a time counter on it.

\subsubsection*{Swamp}
\addcontentsline{toc}{subsubsection}{Swamp}

One of the five basic land types. Any land with this subtype has the ability “{T: Add {B.” See rule 305.6.

\subsubsection*{Swampcycling}
\addcontentsline{toc}{subsubsection}{Swampcycling}

See Typecycling.

\subsubsection*{Swampwalk}
\addcontentsline{toc}{subsubsection}{Swampwalk}

See Landwalk.

\subsubsection*{Tap}
\addcontentsline{toc}{subsubsection}{Tap}

To turn a permanent sideways from an upright position. See rule 701.26, “Tap and Untap.”

\subsubsection*{Tapped}
\addcontentsline{toc}{subsubsection}{Tapped}

A status a permanent may have. See rule 110.5 and rule 701.26, “Tap and Untap.” See also Untapped.

\subsubsection*{Tap Symbol}
\addcontentsline{toc}{subsubsection}{Tap Symbol}

The tap symbol {T in an activation cost means “Tap this permanent.” See rule 107.5.

\subsubsection*{Target}
\addcontentsline{toc}{subsubsection}{Target}

A preselected object or player a spell or ability will affect. See rule 115, “Targets.”

\subsubsection*{Team}
\addcontentsline{toc}{subsubsection}{Team}

A group of players who share a common victory condition in a multiplayer game. See rule 808, “Team vs. Team Variant,” rule 809, “Emperor Variant,” rule 810, “Two-Headed Giant Variant,” and rule 811, “Alternating Teams Variant.”

\subsubsection*{Teammate}
\addcontentsline{toc}{subsubsection}{Teammate}

In a multiplayer game between teams, a player’s teammates are the other players on their team. See rule 102.3.

\subsubsection*{Team vs. Team Variant}
\addcontentsline{toc}{subsubsection}{Team vs. Team Variant}

A multiplayer variant played among two or more teams, each of which sits together. See rule 808, “Team vs. Team Variant.”

\subsubsection*{Text Box}
\addcontentsline{toc}{subsubsection}{Text Box}

Part of a card. The text box is printed on the lower half of the card and contains the card’s rules text, reminder text, and flavor text. See rule 207, “Text Box.”

\subsubsection*{Text-Changing Effect}
\addcontentsline{toc}{subsubsection}{Text-Changing Effect}

A continuous effect that changes the text that appears in an object’s text box and/or type line. See rule 612, “Text-Changing Effects.”

\subsubsection*{Threshold}
\addcontentsline{toc}{subsubsection}{Threshold}

“Threshold” used to be a keyword ability. It is now an ability word and has no rules meaning. All cards printed with the threshold keyword have received errata in the Oracle card reference.

\subsubsection*{Ticket Symbol}
\addcontentsline{toc}{subsubsection}{Ticket Symbol}

The ticket symbol {TK with no numbers in it represents one ticket counter. The ticket symbol with a number in it represents a ticket cost. To pay a ticket cost, a player removes that many ticket counters from themselves.

\subsubsection*{Tiered}
\addcontentsline{toc}{subsubsection}{Tiered}

A keyword ability found on some modal spells that requires you to pay an additional cost for the mode you choose. See rule 702.183, “Tiered.”

\subsubsection*{Time Travel}
\addcontentsline{toc}{subsubsection}{Time Travel}

To add a time counter to or remove a time counter from any number of permanents you control with a time counter on them or suspended cards you own in exile with time counters on them. See rule 701.56, “Time Travel.”

\subsubsection*{Timestamp Order}
\addcontentsline{toc}{subsubsection}{Timestamp Order}

A system used to determine in which order continuous effects in the same layer or sublayer are applied. See rule 613.7. See also Dependency.

\subsubsection*{Token}
\addcontentsline{toc}{subsubsection}{Token}

A marker used to represent any permanent that isn’t represented by a card. See rule 111, “Tokens.”

\subsubsection*{Tombstone Icon}
\addcontentsline{toc}{subsubsection}{Tombstone Icon}

An icon that appears in the upper left of some Odyssey block cards that has no effect on game play. See rule 107.9.

\subsubsection*{Total Casting Cost (Obsolete)}
\addcontentsline{toc}{subsubsection}{Total Casting Cost (Obsolete)}

An obsolete term for mana value. Cards printed with this term have received errata in the Oracle card reference.

\subsubsection*{Total Cost}
\addcontentsline{toc}{subsubsection}{Total Cost}

What a player actually has to pay, in practical terms, to cast a spell or activated ability: the mana cost, activation cost, or alternative cost, plus all cost increases (including additional costs) and minus all cost reductions. See rule 601.2f.

\subsubsection*{Totem Armor (Obsolete)}
\addcontentsline{toc}{subsubsection}{Totem Armor (Obsolete)}

An obsolete keyword ability that has been renamed. See rule 702.89, “Umbra Armor.”

\subsubsection*{Toughness}
\addcontentsline{toc}{subsubsection}{Toughness}

Part of a card that only creature cards have. A creature card’s toughness is printed after the slash in its lower right corner. See rule 208, “Power/Toughness.” A characteristic that only creatures have. See rule 302.4.

\subsubsection*{Tournament}
\addcontentsline{toc}{subsubsection}{Tournament}

An organized play activity where players compete against other players. See rule 100.6.

\subsubsection*{Tournament Rules}
\addcontentsline{toc}{subsubsection}{Tournament Rules}

Additional rules that apply to games played in a sanctioned tournament. See rule 100.6.

\subsubsection*{Toxic}
\addcontentsline{toc}{subsubsection}{Toxic}

A keyword ability that causes a player to get poison counters due to combat damage from creatures with the ability. See rule 702.164, “Toxic.”

\subsubsection*{Traditional Magic Card}
\addcontentsline{toc}{subsubsection}{Traditional Magic Card}

A Magic card that measures approximately 2.5 inches (6.3 centimeters) by 3.5 inches (8.8 centimeters) and is included in players’ decks. See rule 108.2.

\subsubsection*{Training}
\addcontentsline{toc}{subsubsection}{Training}

A keyword ability that means “Whenever this creature and at least one other creature with power greater that this creature’s power attack, put a +1/+1 counter on this creature.” See rule 702.149, “Training.”

\subsubsection*{Trample}
\addcontentsline{toc}{subsubsection}{Trample}

A keyword ability that modifies how a creature assigns combat damage. See rule 702.19, “Trample.”

\subsubsection*{Trample Over Planeswalkers}
\addcontentsline{toc}{subsubsection}{Trample Over Planeswalkers}

A variant of trample that modifies how a creature assigns combat damage if it’s attacking a planeswalker. See rule 702.19, “Trample”

\subsubsection*{Transfigure}
\addcontentsline{toc}{subsubsection}{Transfigure}

A keyword ability that lets a player search their library for a replacement creature card. See rule 702.71, “Transfigure.”

\subsubsection*{Transform}
\addcontentsline{toc}{subsubsection}{Transform}

To turn a double-faced card so its other face is up. See rule 701.27, “Transform.”

\subsubsection*{Transforming Double-Faced Cards (Obsolete)}
\addcontentsline{toc}{subsubsection}{Transforming Double-Faced Cards (Obsolete)}

An older name for nonmodal double-faced cards. See rule 712, “Double-Faced Cards.”

\subsubsection*{Transmute}
\addcontentsline{toc}{subsubsection}{Transmute}

A keyword ability that lets a player search their library for a replacement card. See rule 702.53, “Transmute.”

\subsubsection*{Treasure Token}
\addcontentsline{toc}{subsubsection}{Treasure Token}

A Treasure token is a colorless artifact token with “{T, Sacrifice this token: Add one mana of any color.” For more information about predefined tokens, see rule 111.10.

\subsubsection*{Tribal (Obsolete)}
\addcontentsline{toc}{subsubsection}{Tribal (Obsolete)}

An obsolete card type that has been renamed. See rule 308, “Kindreds.”

\subsubsection*{Tribute}
\addcontentsline{toc}{subsubsection}{Tribute}

A keyword ability that allows an opponent to choose between a creature entering the battlefield with +1/+1 counters or an additional ability. See rule 702.104, “Tribute.”

\subsubsection*{Trigger}
\addcontentsline{toc}{subsubsection}{Trigger}

Whenever a game event or game state matches a triggered ability’s trigger event, that ability automatically “triggers.” That means its controller puts it on the stack the next time a player would receive priority. See rule 603, “Handling Triggered Abilities.”

\subsubsection*{Trigger Condition}
\addcontentsline{toc}{subsubsection}{Trigger Condition}

The first part of a triggered ability, consisting of “when,” “whenever,” or “at” followed by a trigger event. See rule 603, “Handling Triggered Abilities.”

\subsubsection*{Triggered Ability}
\addcontentsline{toc}{subsubsection}{Triggered Ability}

A kind of ability. Triggered abilities begin with the word “when,” “whenever,” or “at.” They’re written as “[Trigger condition], [effect].” See rule 113, “Abilities,” and rule 603, “Handling Triggered Abilities.”

\subsubsection*{Trigger Event}
\addcontentsline{toc}{subsubsection}{Trigger Event}

The event that a triggered ability looks for. Whenever the trigger event occurs, the triggered ability triggers. See rule 603, “Handling Triggered Abilities.”

\subsubsection*{Triple}
\addcontentsline{toc}{subsubsection}{Triple}

A keyword action that increases a creature’s power and/or toughness. See rule 701.11, “Triple.”

\subsubsection*{Turn-Based Actions}
\addcontentsline{toc}{subsubsection}{Turn-Based Actions}

Game actions that happen automatically when certain steps or phases begin, or when each step or phase ends. See rule 703, “Turn-Based Actions.”

\subsubsection*{Turn Markers}
\addcontentsline{toc}{subsubsection}{Turn Markers}

Markers used to keep track of which players are taking turns in a Grand Melee game. See rule 807.4.

\subsubsection*{Two-Headed Giant Variant}
\addcontentsline{toc}{subsubsection}{Two-Headed Giant Variant}

A multiplayer variant played among two-player teams that each have a shared life total and take a simultaneous turn. See rule 810, “Two-Headed Giant Variant.”

\subsubsection*{Type}
\addcontentsline{toc}{subsubsection}{Type}

An object’s card type or, more broadly, its card type, subtype, and/or supertype. See rule 205, “Type Line,” and section 3, “Card Types.”
An attribute mana has. See rule 106, “Mana.”

\subsubsection*{Type Icon}
\addcontentsline{toc}{subsubsection}{Type Icon}

An icon that appears in the upper left of some Future Sight cards that has no effect on game play. See rule 107.10.

\subsubsection*{Type Line}
\addcontentsline{toc}{subsubsection}{Type Line}

Part of a card. The type line is printed directly below the illustration and contains the card’s card type(s), subtype(s), and/or supertype(s). See rule 205, “Type Line.”

\subsubsection*{Type-Changing Effect}
\addcontentsline{toc}{subsubsection}{Type-Changing Effect}

An effect that changes an object’s card type, subtype, and/or supertype. See rules 205.1a–b, 305.7, and 613.1d.

\subsubsection*{Typecycling}
\addcontentsline{toc}{subsubsection}{Typecycling}

A variant of the cycling ability. See rule 702.29, “Cycling.”

\subsubsection*{Umbra Armor}
\addcontentsline{toc}{subsubsection}{Umbra Armor}

A keyword ability that allows an Aura to protect the permanent it’s enchanting. See rule 702.89, “Umbra Armor.”

\subsubsection*{Unattach}
\addcontentsline{toc}{subsubsection}{Unattach}

To move an Equipment away from the creature it’s attached to so that the Equipment is on the battlefield but is not equipping anything. See rule 701.3d.

\subsubsection*{Unblockable (Obsolete)}
\addcontentsline{toc}{subsubsection}{Unblockable (Obsolete)}

A term that meant “can’t be blocked.” Cards that used this term have received errata in the Oracle card reference.

\subsubsection*{Unblocked Creature}
\addcontentsline{toc}{subsubsection}{Unblocked Creature}

An attacking creature once no creature has been declared as a blocker for it, unless an effect has caused it to become blocked. It remains an unblocked creature until it’s removed from combat or the combat phase ends, whichever comes first. See rule 509, “Declare Blockers Step.”

\subsubsection*{Undaunted}
\addcontentsline{toc}{subsubsection}{Undaunted}

A keyword ability that reduces the cost of a spell based on the number of opponents you have. See rule 702.125, “Undaunted.”

\subsubsection*{Undying}
\addcontentsline{toc}{subsubsection}{Undying}

A keyword ability that can return a creature from the graveyard to the battlefield. See rule 702.93, “Undying.”

\subsubsection*{Unearth}
\addcontentsline{toc}{subsubsection}{Unearth}

A keyword ability that lets a player return a creature card from their graveyard to the battlefield. See rule 702.84, “Unearth.”

\subsubsection*{Unflipped}
\addcontentsline{toc}{subsubsection}{Unflipped}

A default status a permanent may have. See rule 110.5 and rule 710, “Flip Cards.” See also Flipped.

\subsubsection*{Unleash}
\addcontentsline{toc}{subsubsection}{Unleash}

A keyword ability that allows a creature to enter the battlefield with a +1/+1 counter on it and stops it from blocking if it has a +1/+1 counter on it. See rule 702.98, “Unleash.”

\subsubsection*{Unless}
\addcontentsline{toc}{subsubsection}{Unless}

A word used to indicate a certain style of cost. See rule 118.12a.

\subsubsection*{Unlock}
\addcontentsline{toc}{subsubsection}{Unlock}

To give an unlocked designation to a permanent that has one or more locked halves. See rule 709.5f.

\subsubsection*{Unlocked}
\addcontentsline{toc}{subsubsection}{Unlocked}

One half of a split permanent is “unlocked” if it has the appropriate unlocked designation. See rule 709.5.

\subsubsection*{Untap}
\addcontentsline{toc}{subsubsection}{Untap}

To rotate a permanent back to the upright position from a sideways position. See rule 701.26, “Tap and Untap.”

\subsubsection*{Untap Step}
\addcontentsline{toc}{subsubsection}{Untap Step}

Part of the turn. This step is the first step of the beginning phase. See rule 502, “Untap Step.”

\subsubsection*{Untap Symbol}
\addcontentsline{toc}{subsubsection}{Untap Symbol}

The untap symbol {Q in an activation cost means “Untap this permanent.” See rule 107.6.

\subsubsection*{Untapped}
\addcontentsline{toc}{subsubsection}{Untapped}

A default status a permanent may have. See rule 110.5 and rule 701.26, “Tap and Untap.” See also Tapped.

\subsubsection*{Upkeep Step}
\addcontentsline{toc}{subsubsection}{Upkeep Step}

Part of the turn. This step is the second step of the beginning phase. See rule 503, “Upkeep Step.”

\subsubsection*{Vancouver Mulligan}
\addcontentsline{toc}{subsubsection}{Vancouver Mulligan}

Informal term for a previous system of taking a mulligan. Using the Vancouver mulligan, a player who took a mulligan shuffled their hand into their library and drew one fewer card. After choosing to not mulligan, a player who took a mulligan looked at the top card of their library and could put it on the bottom of their library. For current mulligan rules, see rule 103.5.

\subsubsection*{Vanguard}
\addcontentsline{toc}{subsubsection}{Vanguard}

A casual variant in which each player plays the role of a famous character. See rule 902, “Vanguard.”
A card type seen only on nontraditional Magic cards in the Vanguard casual variant. A vanguard card is not a permanent. See rule 313, “Vanguards.”
Vanishing

A keyword ability that limits how long a permanent remains on the battlefield. See rule 702.63, “Vanishing.”

\subsubsection*{Variant}
\addcontentsline{toc}{subsubsection}{Variant}

An additional set of rules that determines the style of a multiplayer game. See rule 800.2.

\subsubsection*{Vehicle}
\addcontentsline{toc}{subsubsection}{Vehicle}

An artifact subtype. Vehicles can become artifact creatures. See rule 301, “Artifacts,” and rule 702.122, “Crew.”

\subsubsection*{Venture into [Quality]}
\addcontentsline{toc}{subsubsection}{Venture into [Quality]}

A variant of the venture into the dungeon ability that allows a player to bring a dungeon card with [quality] into the game or move a player’s venture marker. See rule 701.49, “Venture into the Dungeon.”

\subsubsection*{Venture into the Dungeon}
\addcontentsline{toc}{subsubsection}{Venture into the Dungeon}

A keyword action that can bring dungeon cards into the game from outside the game or move a player’s venture marker. See rule 701.49, “Venture into the Dungeon.”

\subsubsection*{Venture Marker}
\addcontentsline{toc}{subsubsection}{Venture Marker}

A marker used to track which room of a dungeon card a player is currently in. See rule 309, “Dungeons.”

\subsubsection*{Vigilance}
\addcontentsline{toc}{subsubsection}{Vigilance}

A keyword ability that lets a creature attack without tapping. See rule 702.20, “Vigilance.”

\subsubsection*{Visit}
\addcontentsline{toc}{subsubsection}{Visit}

A keyword ability found on Attraction cards. It provides an effect whenever you roll to visit your attractions and get certain results. See rule 702.159, “Visit.”

\subsubsection*{Vote}
\addcontentsline{toc}{subsubsection}{Vote}

Some cards instruct players to vote from among given options. See rule 701.38, “Vote.”

\subsubsection*{Walker Token}
\addcontentsline{toc}{subsubsection}{Walker Token}

A Walker token is a 2/2 black Zombie creature token named Walker. For more information on predefined tokens, see rule 111.10.

\subsubsection*{Wall}
\addcontentsline{toc}{subsubsection}{Wall}

A creature type with no particular rules meaning. Older cards with the Wall creature type but without defender had an unwritten ability that precluded them from attacking. Those cards have received errata in the Oracle card reference to have defender. Some older cards that referenced the Wall creature type have also received errata. See Defender.

\subsubsection*{Ward}
\addcontentsline{toc}{subsubsection}{Ward}

A triggered ability that can counter spells or abilities that target the permanent with ward. See rule 702.21, “Ward.”

\subsubsection*{Warp}
\addcontentsline{toc}{subsubsection}{Warp}

A keyword ability found on permanent cards that allows them to be cast for an alternative cost. See rule 702.185, “Warp.”

\subsubsection*{Waterbend}
\addcontentsline{toc}{subsubsection}{Waterbend}

A keyword action. “Waterbend [cost]” means to pay that cost and, for each {1 in that cost, you may tap an untapped artifact or creature you control rather than pay mana. See rule 701.67, “Waterbend.”

\subsubsection*{Web-slinging}
\addcontentsline{toc}{subsubsection}{Web-slinging}

A keyword ability that allows spells to be cast for an alternative cost by returning a tapped creature you control to its owner’s hand. See rule 702.188, “Web-slinging.”

\subsubsection*{Win the Game}
\addcontentsline{toc}{subsubsection}{Win the Game}

There are several ways to win the game. See rule 104, “Ending the Game,” and rules 810.8 (for additional rules for Two-Headed Giant games) and rule 809.5 (for additional rules for Emperor games).

\subsubsection*{Wither}
\addcontentsline{toc}{subsubsection}{Wither}

A keyword ability that affects how an object deals damage to a creature. See rule 702.80, “Wither.”

\subsubsection*{Wizardcycling}
\addcontentsline{toc}{subsubsection}{Wizardcycling}

See Typecycling.

\subsubsection*{World}
\addcontentsline{toc}{subsubsection}{World}

A supertype that’s normally relevant on enchantments. See rule 205.4, “Supertypes.” See also World Rule.

\subsubsection*{World Rule}
\addcontentsline{toc}{subsubsection}{World Rule}

A state-based action that causes all permanents with the world supertype except the one that has had the world supertype for the shortest amount of time are put into their owners’ graveyards. See rule 704.5k.

\subsubsection*{X}
\addcontentsline{toc}{subsubsection}{X}

A placeholder for a number that needs to be determined. See rule 107.3.

\subsubsection*{Y}
\addcontentsline{toc}{subsubsection}{Y}

See X.

\subsubsection*{You, Your}
\addcontentsline{toc}{subsubsection}{You, Your}

Words that refer to an object’s controller, its would-be controller (if a player is attempting to cast or activate it), or its owner (if it has no controller). See rule 109.5.

\subsubsection*{Zone}
\addcontentsline{toc}{subsubsection}{Zone}

A place where objects can be during a game. See section 4, “Zones.”

\subsubsection*{Zone-Change Triggers}
\addcontentsline{toc}{subsubsection}{Zone-Change Triggers}

Trigger events that involve objects changing zones. See rule 603.6.